---
title: "Antibiotics and Delay Duration Report"
date: '`r strftime(Sys.time(), format = "%B %d, %Y")`'
output: html_document
params:
  cond:
    value: x
---

```{r setup, include=FALSE}
knitr::opts_chunk$set(
      echo    = FALSE
    , warning = FALSE
    , message = FALSE
)

library(tidyverse)
library(kableExtra)
library(ggplot2)
library(lubridate)

# params <- list()
# params$cond <- "tb"

# load delay_parms
# load("/Shared/AML/params/delay_any_params.RData")

delay_params <- delay_any_params[[params$cond]]

delay_base_path <- paste0("/Shared/Statepi_Diagnosis/prelim_results/",params$cond,"/delay_results/")

# load(paste0(delay_base_path,"abx_duration_models.RData"))

```

# Antibiotic Delay Report for `r params$cond`

The following are results for estimates of the effect of antibiotics on the diagnostic
delay duration

### Any antibiotic visit

The following results estimate the effect of receiving any antibiotic during the 
diagnostic opportunity window on the duration of diagnostic delay.

Model 1 represents having received an antibiotic during the individual-specific 
diagnostic opportunity window (i.e., the time between the patients first diagnostic 
opportunity and the index diagnosis)

Model 2 represents having received an antibiotic at any point during the entire
diagnostic opportunity window; in this case, during the `r delay_params$cp` days
prior to diagnosis. Note: this model does not restrict antibiotics to each individual's
specific opportunity window.

```{r, echo = FALSE}
tmp1 <- abx_delay_res$any_abx1 %>% 
  mutate_at(vars(mdn_est:hi_est), ~round(.,2)) %>% 
  mutate(`Model 1` = paste0(mn_est," (",lo_est,"-",hi_est,")")) %>% 
  select(Coef = name,`Model 1`)

tmp2 <- abx_delay_res$any_abx2 %>% 
  mutate_at(vars(mdn_est:hi_est), ~round(.,2)) %>% 
  mutate(`Model 2` = paste0(mn_est," (",lo_est,"-",hi_est,")")) %>% 
  select(Coef = name,`Model 2`)

inner_join(tmp1,tmp2) %>% 
  kableExtra::kable() %>% 
  kableExtra::kable_styling(full_width = F)

```


### Antibiotic Days Supplied

The following models estimate the effect of the number of antibiotic days supplied
for antibiotics received during the diagnostic opportunity window on the duration
of diagnostic delay.

Similar to above, Models 1 and 2 represent using the individual-specific diagnostic
opportunity window (Model 1) and the overall diagnostic opportunity window (Model2).

```{r, echo = FALSE}
tmp1 <- abx_delay_res$abx_dur1 %>% 
  mutate_at(vars(mdn_est:hi_est), ~round(.,2)) %>% 
  mutate(`Model 1` = paste0(mn_est," (",lo_est,"-",hi_est,")")) %>% 
  select(Coef = name,`Model 1`)

tmp2 <- abx_delay_res$abx_dur2 %>% 
  mutate_at(vars(mdn_est:hi_est), ~round(.,2)) %>% 
  mutate(`Model 2` = paste0(mn_est," (",lo_est,"-",hi_est,")")) %>% 
  select(Coef = name,`Model 2`)

inner_join(tmp1,tmp2) %>% 
  kableExtra::kable() %>% 
  kableExtra::kable_styling(full_width = F)

```


### Categories of Antibiotic Days Supplied

The following models estimate the effect of the number of antibiotic days supplied
for antibiotics received during the diagnostic opportunity window on the duration
of diagnostic delay. However, in contrast to the model above, here we group antibiotic
days supplied into separate categories representing commonly prescribed days of use.

Similar to above, Models 1 and 2 represent using the individual-specific diagnostic
opportunity window (Model 1) and the overall diagnostic opportunity window (Model2).

```{r, echo = FALSE}
tmp1 <- abx_delay_res$abx_cats1 %>% 
  mutate_at(vars(mdn_est:hi_est), ~round(.,2)) %>% 
  mutate(`Model 1` = paste0(mn_est," (",lo_est,"-",hi_est,")")) %>% 
  select(Coef = name,`Model 1`)

tmp2 <- abx_delay_res$abx_cats2 %>% 
  mutate_at(vars(mdn_est:hi_est), ~round(.,2)) %>% 
  mutate(`Model 2` = paste0(mn_est," (",lo_est,"-",hi_est,")")) %>% 
  select(Coef = name,`Model 2`)

tibble(Coef = c("(Intercept)","abx_days_cat1-3","abx_days_cat4-5","abx_days_cat6-7",
                "abx_days_cat8-10","abx_days_cat11-14","abx_days_cat>14","age_cat(17,34]",
                "age_cat(34,44]","age_cat(44,54]","age_cat(54,64]","age_cat(64,130]",
                "sexmale"),
       Coefficient = c("(Intercept)","abx 1-3 days","abx 4-5 days","abx 6-7 days",
                "abx 8-10 days","abx 11-13 days","abx >13 days","age_cat(17,34]",
                "age_cat(34,44]","age_cat(44,54]","age_cat(54,64]","age_cat(64,130]",
                "sexmale")) %>%
  inner_join(inner_join(tmp1,tmp2)) %>% 
  select(-Coef) %>% 
  kableExtra::kable() %>% 
  kableExtra::kable_styling(full_width = F)

```
