---
title: "Delay Report for Sepsis (pre-COVID)"
date: '`r strftime(Sys.time(), format = "%B %d, %Y")`'
output: html_document
---

```{r setup, include=FALSE}
knitr::opts_chunk$set(
      echo    = FALSE
    , warning = FALSE
    , message = FALSE
)

library(tidyverse)
library(kableExtra)
library(ggplot2)
library(lubridate)

cond_name <- "sepsis_pre_covid"

load("/Shared/AML/params/final_delay_params.RData")

delay_params <- final_delay_params[[cond_name]]

sim_out_path <- paste0(delay_params$out_path,"sim_results/")

# Load Index cases
load(paste0(delay_params$out_path,"index_cases.RData"))

n_patients <- nrow(index_cases)

```

The following report summarizes the final simulation results for diagnostic delays
associated with hospitalized sepsis cases.

For this analysis we used the case definition provided in Jolley RJ, et al. [BMJ Open 2015;5:e009487] 
to identify cases of sepsis. Cases were identified specifically based on index diagnoses 
that resulted in a hospital admission. We focus on the index case (i.e., the first 
diagnosis) in each individual and exclude individuals who had a prior sepsis diagnosis 
recorded only in an outpatient setting. We also include individuals who received a sepsis 
diagnosis in an outpatient setting followed by a hospital admission for sepsis
within 7 days of the index sepsis diagnosis.

Given the above case definition, we focus exclusively on sepsis events recorded 
using ICD-10 codes from 2016-2019 (we exclude sepsis events during the COVID-19 
pandemic. We identify all inpatient, outpatient and ED events recorded in the 
180 days prior to the index diagnosis. We exlucded sepsis cases that did not have 
continuous enrollment for at least 180 days prior to the index sepsis event. Thus, 
we also exclude sepsis cases that occured in the first 180 days of 2016.

# Summary Statistics

There were a total of `r n_patients` cases of sepsis identified from 2016-2019 that
met the above inclusion criteria.

The following table summarizes the study population:
```{r}
load(paste0(sim_out_path,"report_data/baseline_data.RData"))
baseline_data$pat_char %>%   
  kableExtra::kable() %>% 
  kableExtra::kable_styling(full_width = F) 
```

The following table summarizes the time of the index sepsis diagnoses:
```{r}
baseline_data$index_char %>%   
  kableExtra::kable() %>% 
  kableExtra::kable_styling(full_width = F) 
```


The following plot depicts the number of index cases identified each week over
the study period:
```{r}
index_cases %>% 
  mutate(index_week = 7*(index_date %/% 7)) %>% 
  mutate(index_week = as_date(index_week)) %>% 
  count(index_week) %>% 
  ggplot(aes(index_week,n)) +
  geom_line()
```

# Visit Trends

We identified all visits that occurred in the 180 days prior to the index sepsis 
diagnosis and then filtered to those visits that contained a sign, symptom or
symptomatically similar diagnosis (SSD) to sepsis. The following plot depicts the
trend in the number of all visits and SSD-related visits over the 180 days prior
to the index diagnosis:
```{r}
load(paste0(sim_out_path,"report_data/trends_output.RData"))
load(paste0(sim_out_path,"trends/fit_trends.RData"))

trends_ssd <- ssd_vis_count_fitted %>% 
  rename(tot_miss=num_miss) %>% 
  unnest(counts) %>% 
  mutate(model_label = paste0(model," (CP = ",cp," days)"))

mse_res_ssd <- trends_ssd %>%
  filter(is.na(num_miss)) %>% 
  group_by(model_label) %>% 
  summarise(rmse = sqrt(mean((pred-n)^2))) %>% 
  mutate(label = paste("RMSE: ", round(rmse,2)))

trends_all <- all_vis_count_fitted %>% 
  rename(tot_miss=num_miss) %>% 
  unnest(counts) %>% 
  mutate(model_label = paste0(model," (CP = ",cp," days)"))

mse_res_all <- trends_all %>%
  filter(is.na(num_miss)) %>% 
  group_by(model_label) %>% 
  summarise(rmse = sqrt(mean((pred-n)^2))) %>% 
  mutate(label = paste("RMSE: ", round(rmse,2)))

bind_rows(trends_ssd %>% 
            filter(cp ==7, model=="exponential") %>% 
            select(period,n) %>% 
            mutate(group = "SSD Visits"),
          trends_all %>% 
            filter(cp ==7, model=="exponential") %>% 
            select(period,n) %>% 
            mutate(group = "All Visits")) %>% 
  ggplot(aes(period,n)) +
  geom_line() +
  scale_x_reverse() +
  facet_wrap(~group, scale = "free_y") +
  ylab("Number of visits") +
  xlab("Days before index sepsis diagnosis") +
  theme_bw() 
  


```


### Expected SSD-visit trends

We used an exponential model to estimate the expected number of visits prior each
day prior to the index diagnosis. Our primary analysis used a 14-day diagnostic 
opportunity window (i.e., change-point) to detect diagnostic delays; thus, the 
expected visit trend was estimated using the visits observed from 15 to 180 days
prior to the index diagnosis.

As a sensitivity analysis we considered using a 7-day diagnostic opportunity window.

The following plot depicts the number of SSD visits each day before the index
sepsis diagnosis (black line), along with the estimated expected visit trend (red
line) for both the 14-and 7-day diagnostic opportunity window. The dashed-black 
line depicts the boundary of the diagnostic opportunity window.

```{r}

y_pos <- .9*max(trends_ssd$n)
x_pos <- .8*180


trends_ssd %>%
  ggplot(aes(period,n)) +
  geom_line() +
  scale_x_reverse() +
  geom_line(aes(y = pred), color = "red") +
  facet_wrap(~model_label) +
  geom_vline(aes(xintercept = cp), linetype =2) +
  theme_bw() +
  geom_text(data = mse_res_ssd,
            mapping = aes(x = x_pos, y = y_pos, label = label)) +
  ylab("Number of SSD visits") +
  xlab("Days before index sepsis diagnosis")
```

The following figure depicts the estimated number of missed opportunities each
day during the diagnostic opportunity window for both the 14- and 7- day windows.

```{r}


```



# Primary Bootstrapping Results
To estimate aggregate and individual-level statistics we performed a bootstrapping
procedure to repeatedly draw which individual visits represented a diagnostic delay.
For this analysis we performed a 2-layer bootstrapping procedure. For the outer 
layer we drew a bootstrapped sample of patients from the overall cohort (with replacement).
We then re-estimated the expected visit trend, and computed the estimated number 
of missed opportunities each day for each bootstrapped sample. Next for each bootstrapped
sample we run an interior bootstrapping procedure were we randomly select which 
visits represent a missed opportunity each day based on the estimated number of 
missed opportunities. 

We run 100 trials of the outer bootstrapping procedure and 100 trials of the interior
procedure for a total of 10,000 simulations. We then aggregate results across all
trials to compute mean estimates and 95% quantile-based confidence intervals


### Overview

The following table summarizes the overall results for the primary model (exponential
trend and 14 day opportunity window) for the number and percent of patients that 
were missed, duration of diagnostic delays, and the number of missed opportunities 
that patients experienced. Note: both the duration of delays and number of missed 
opportunities per patient are summarized across only those patients who experienced
a diagnostic delay:
```{r}
# load(paste0(sim_out_path, "report_data/agg_stats.RData"))
# 
# better_labels <- tibble(measure = c("pct_pat","n_pat","mean_dur","median_dur","mean_n_miss","median_n_miss"),
#                         Measure = c("Percent of patients w/ miss", "Number of patients w/ miss","Mean duration of delay", "Median duration of delay",
#                                     "Mean # of misses (per patient w/ miss)", "Median # of misses (per patient w/ miss)"))
# 
# tmp1 <- agg_stats$exponential_14$agg_stats_ssd$main_stats %>% 
#   inner_join(better_labels) %>% 
#   select(Measure, `Exponential 14-day CP`=measure_out)
# 
# tmp2 <- agg_stats$exponential_7$agg_stats_ssd$main_stats %>% 
#   inner_join(better_labels) %>% 
#   select(Measure, `Exponential 7-day CP`=measure_out)
# 
# inner_join(tmp1,tmp2,by = join_by(Measure)) %>% 
#   filter(Measure !="Number of patients w/ miss") %>% 
#   kableExtra::kable() %>% 
#   kableExtra::kable_styling(full_width = F) 

agg_stats$exponential_14$agg_stats_ssd$main_stats %>% 
  inner_join(better_labels) %>% 
  select(Measure, `Estimate (95% CI)`=measure_out) %>% 
  kableExtra::kable() %>% 
  kableExtra::kable_styling(full_width = F)

```


The following table presents the distribution of delay duration:
```{r}
agg_stats$exponential_14$agg_stats_ssd$duration_bins %>% 
  mutate(Duration = paste0(">= ", duration_bin," days")) %>% 
  rename(`Number of patients`=n, `Percent of all patients`=pct_all,
         `Percent of patients w/ miss` = pct_miss) %>% 
  select(-duration_bin) %>% 
  select(Duration, everything()) %>% 
  kableExtra::kable() %>% 
  kableExtra::kable_styling(full_width = F)
```

The following table presents the distribution of the number of missed opportunities 
that individual patients experienced:
```{r}
agg_stats$exponential_14$agg_stats_ssd$miss_bins %>% 
  mutate(`Number of misses` = paste0(">= ", miss_bin)) %>% 
  rename(`Number of patients`=n, `Percent of all patients`=pct_all,
         `Percent of patients w/ miss` = pct_miss) %>% 
  select(-miss_bin) %>% 
  select(`Number of misses`, everything()) %>% 
  kableExtra::kable() %>% 
  kableExtra::kable_styling(full_width = F)
```


# Sensitivity Analysis - Exponential trend w/ 7-day change-point

We also conducted a sensitivity analysis where we considered a 7-day diagnostic 
opportunity window. The following table presents the aggregated summary statistics
for this sensitivity analysis.
```{r}
agg_stats$exponential_7$agg_stats_ssd$main_stats %>% 
  inner_join(better_labels) %>% 
  select(Measure, `Estimate (95% CI)`=measure_out) %>% 
  kableExtra::kable() %>% 
  kableExtra::kable_styling(full_width = F)

```

The following table presents the distribution of delay duration:
```{r}
agg_stats$exponential_7$agg_stats_ssd$duration_bins %>% 
  filter(duration_bin<=7) %>% 
  mutate(Duration = paste0(">= ", duration_bin," days")) %>% 
  rename(`Number of patients`=n, `Percent of all patients`=pct_all,
         `Percent of patients w/ miss` = pct_miss) %>% 
  select(-duration_bin) %>% 
  select(Duration, everything()) %>% 
  kableExtra::kable() %>% 
  kableExtra::kable_styling(full_width = F)
```

The following table presents the distribution of the number of missed opportunities 
that individual patients experienced:
```{r}
agg_stats$exponential_7$agg_stats_ssd$miss_bins %>% 
  mutate(`Number of misses` = paste0(">= ", miss_bin)) %>% 
  rename(`Number of patients`=n, `Percent of all patients`=pct_all,
         `Percent of patients w/ miss` = pct_miss) %>% 
  select(-miss_bin) %>% 
  select(`Number of misses`, everything()) %>% 
  kableExtra::kable() %>% 
  kableExtra::kable_styling(full_width = F)
```


# Appendix - Results using All visits

### Expected Visits Trends

As an alternative sensitivity analysis we analyzed all visits, regardless of whether
an SSD was present. We then re-fit the expected trend curves. The following figures 
depict the observed and expected trends in SSD visits.

```{r}

y_pos <- .9*max(trends_all$n)


trends_all %>%
  ggplot(aes(period,n)) +
  geom_line() +
  scale_x_reverse() +
  geom_line(aes(y = pred), color = "red") +
  facet_wrap(~model_label) +
  geom_vline(aes(xintercept = cp), linetype =2) +
  theme_bw() +
  geom_text(data = mse_res_all,
            mapping = aes(x = x_pos, y = y_pos, label = label)) +
  ylab("Number of visits (any reason)") +
  xlab("Days before index sepsis diagnosis")
```

The following table summarize the model fit and implied number of missed opportunities
across models, change-points, and visit types.

```{r}
trends_out$model_comparisons_table %>% 
  kableExtra::kable() %>% 
  kableExtra::kable_styling(full_width = F)

```


### Primary Model - Exponential trend w/ 14-day change-point

The following table presents the aggregated summary statistics
```{r}
agg_stats$exponential_14$agg_stats_all$main_stats %>% 
  inner_join(better_labels) %>% 
  select(Measure, `Estimate (95% CI)`=measure_out) %>% 
  kableExtra::kable() %>% 
  kableExtra::kable_styling(full_width = F)

```

The following table presents the distribution of delay duration:
```{r}
agg_stats$exponential_14$agg_stats_all$duration_bins %>% 
  mutate(Duration = paste0(">= ", duration_bin," days")) %>% 
  rename(`Number of patients`=n, `Percent of all patients`=pct_all,
         `Percent of patients w/ miss` = pct_miss) %>% 
  select(-duration_bin) %>% 
  select(Duration, everything()) %>% 
  kableExtra::kable() %>% 
  kableExtra::kable_styling(full_width = F)
```

The following table presents the distribution of the number of missed opportunities 
that individual patients experienced:
```{r}
agg_stats$exponential_14$agg_stats_all$miss_bins %>% 
  mutate(`Number of misses` = paste0(">= ", miss_bin)) %>% 
  rename(`Number of patients`=n, `Percent of all patients`=pct_all,
         `Percent of patients w/ miss` = pct_miss) %>% 
  select(-miss_bin) %>% 
  select(`Number of misses`, everything()) %>% 
  kableExtra::kable() %>% 
  kableExtra::kable_styling(full_width = F)
```

### Sensitivity Analysis - Exponential trend w/ 7-day change-point

The following table presents the aggregated summary statistics
```{r}
agg_stats$exponential_7$agg_stats_all$main_stats %>% 
  inner_join(better_labels) %>% 
  select(Measure, `Estimate (95% CI)`=measure_out) %>% 
  kableExtra::kable() %>% 
  kableExtra::kable_styling(full_width = F)

```

The following table presents the distribution of delay duration:
```{r}
agg_stats$exponential_7$agg_stats_all$duration_bins %>% 
  filter(duration_bin<=7) %>% 
  mutate(Duration = paste0(">= ", duration_bin," days")) %>% 
  rename(`Number of patients`=n, `Percent of all patients`=pct_all,
         `Percent of patients w/ miss` = pct_miss) %>% 
  select(-duration_bin) %>% 
  select(Duration, everything()) %>% 
  kableExtra::kable() %>% 
  kableExtra::kable_styling(full_width = F)
```

The following table presents the distribution of the number of missed opportunities 
that individual patients experienced:
```{r}
agg_stats$exponential_7$agg_stats_all$miss_bins %>% 
  mutate(`Number of misses` = paste0(">= ", miss_bin)) %>% 
  rename(`Number of patients`=n, `Percent of all patients`=pct_all,
         `Percent of patients w/ miss` = pct_miss) %>% 
  select(-miss_bin) %>% 
  select(`Number of misses`, everything()) %>% 
  kableExtra::kable() %>% 
  kableExtra::kable_styling(full_width = F)
```

