---
title: "Sepsis - Risk Factor Results"
output: html_document
date: "`r Sys.Date()`"
---

```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = TRUE)
library(tidyverse)
dur1 <- read_csv("/Volumes/Statepi_Diagnosis/projects/sepsis_revised10/pre_covid/sim_results/exponential_cp14/model1_duration_estimate.csv")
dur2 <- read_csv("/Volumes/Statepi_Diagnosis/projects/sepsis_revised10/pre_covid/sim_results/exponential_cp14/model2_duration_estimate.csv")
miss_pat1 <- read_csv("/Volumes/Statepi_Diagnosis/projects/sepsis_revised10/pre_covid/sim_results/exponential_cp14/model1_estimate.csv")
miss_pat2 <- read_csv("/Volumes/Statepi_Diagnosis/projects/sepsis_revised10/pre_covid/sim_results/exponential_cp14/model2_estimate.csv")
```

## Overview

We considered two different risk factor models.

1.  Any Delay - This model estimates the odds that a patient would experience a diagnostic delay of any duration. This model utilized a logistic regression and the effect estimates are presented as odds ratios.

2.  Duration - This model estimates the duration of delay (in days) that patients experienced. Patients that experiences no delay were assigned a delay duration of 0 days. The current results utilize an OLS model, so the results are interpretable in terms of days.

## Models with comorbidity score

The following models utilize a comorbidity score, which is a sum across all 30 Elixhauser comorbidity indicators (i.e., patients could have a score between 0-30)

```{r, echo = FALSE, message=FALSE}
tmp1 <- miss_pat2 %>% 
  mutate_at(vars(or:conf.high),~round(.,2)) %>% 
  mutate(out = paste0(or," (",conf.low,"-",conf.high,")")) %>% 
  select(term,out) %>% 
  rename(`Any Delay (Odds Ratio)`=out)


tmp2 <- dur2 %>% 
  mutate_at(vars(estimate:conf.high),~round(.,2)) %>% 
  mutate(out = paste0(estimate," (",conf.low,"-",conf.high,")")) %>% 
  select(term,out) %>% 
  rename(`Duration Estimate (Days)`=out)

read_csv("/Volumes/Statepi_Diagnosis/projects/sepsis_revised10/pre_covid/sim_results/exponential_cp14/model_labels2.csv") %>% 
  left_join(tmp1 %>% 
              inner_join(tmp2)) %>% 
  mutate(`Any Delay (Odds Ratio)` = ifelse(reference==TRUE,"(REFERENCE)",`Any Delay (Odds Ratio)`)) %>% 
  mutate(`Duration Estimate (Days)` = ifelse(reference==TRUE,"(REFERENCE)",`Duration Estimate (Days)`)) %>% 
  mutate_at(vars(`Any Delay (Odds Ratio)`,`Duration Estimate (Days)`),~replace_na(.,"")) %>% 
  select(-term, -space, -reference) %>% 
  kableExtra::kable() %>% 
  kableExtra::kable_styling(full_width = F) 
```

## Models with comorbidity indicators

The following models utilize comorbidity indicators - there 30 indicators, one for each of the Elixhauser comorbidities.

```{r, echo = FALSE, message=FALSE}
tmp1 <- miss_pat1 %>% 
  mutate_at(vars(or:conf.high),~round(.,2)) %>% 
  mutate(out = paste0(or," (",conf.low,"-",conf.high,")")) %>% 
  select(term,out) %>% 
  rename(`Any Delay (Odds Ratio)`=out)


tmp2 <- dur1 %>% 
  mutate_at(vars(estimate:conf.high),~round(.,2)) %>% 
  mutate(out = paste0(estimate," (",conf.low,"-",conf.high,")")) %>% 
  select(term,out) %>% 
  rename(`Duration Estimate (Days)`=out)

read_csv("/Volumes/Statepi_Diagnosis/projects/sepsis_revised10/pre_covid/sim_results/exponential_cp14/model_labels1.csv") %>% 
  left_join(tmp1 %>% 
              inner_join(tmp2)) %>% 
  mutate(label = ifelse(space==TRUE,paste0("   ",label), label)) %>% 
  mutate(`Any Delay (Odds Ratio)` = ifelse(reference==TRUE,"(REFERENCE)",`Any Delay (Odds Ratio)`)) %>% 
  mutate(`Duration Estimate (Days)` = ifelse(reference==TRUE,"(REFERENCE)",`Duration Estimate (Days)`)) %>% 
  mutate_at(vars(`Any Delay (Odds Ratio)`,`Duration Estimate (Days)`),~replace_na(.,"")) %>% 
  select(-term, -space, -reference) %>% 
  kableExtra::kable() %>% 
  kableExtra::kable_styling(full_width = F) 
```
