---
title: "Delay Report for Sepsis"
date: '`r strftime(Sys.time(), format = "%B %d, %Y")`'
output: html_document
---

```{r setup, include=FALSE}
knitr::opts_chunk$set(
      echo    = FALSE
    , warning = FALSE
    , message = FALSE
)

library(tidyverse)
library(kableExtra)
library(ggplot2)
library(lubridate)

cond_name <- "sepsis_revised10"

load("/Shared/AML/params/final_delay_params.RData")

delay_params <- final_delay_params[[cond_name]]

sim_out_path <- paste0(delay_params$out_path,"sim_results/")

# Load Index cases
load(paste0(delay_params$out_path,"index_cases.RData"))

n_patients <- nrow(index_cases)

```

# Final Diagnostic Delay Report for Sepsis
The following report summarizes the final simulation results for diagnostic delays
associated with hospitalized sepsis cases.

For this analysis we used the case definition provided in Jolley RJ, et al. [BMJ Open 2015;5:e009487] 
to identify cases of sepsis. Cases were identified specifically based on index diagnoses 
that resulted in a hospital admission. We focus on the index case (i.e., the first 
diagnosis) in each individual and exclude individuals who had a prior sepsis diagnosis 
recorded only in an outpatient setting. We also include individuals who received a sepsis 
diagnosis in an outpatient setting followed by a hospital admission for sepsis
within 7 days of the index sepsis diagnosis.

Given the above case definition, we focus exclusively on sepsis events recorded 
using ICD-10 codes from 2016-2021. We identify all inpatient, outpatient and ED 
events recorded in the 180 days prior to the index diagnosis. We exlucded sepsis
cases that did not have continuous enrollment for at least 180 days prior to the
index sepsis event. Thus, we also exclude sepsis cases that occured in the first 
180 days of 2016.

# Summary Statistics

There were a total of `r n_patients` cases of sepsis identified from 2016-2021 that
met the above inclusion criteria.

The following plot depicts the number of index cases identified by each week over
the study period:
```{r}
index_cases %>% 
  mutate(index_week = 7*(index_date %/% 7)) %>% 
  mutate(index_week = as_date(index_week)) %>% 
  count(index_week) %>% 
  ggplot(aes(index_week,n)) +
  geom_line()
```

We identified all visits that occurred in the 180 days prior to the index sepsis 
diagnosis and then filtered to those visits that contained a sign, symptom or
symptomatically similar diagnosis (SSD) to sepsis. The following plot depicts the
trend in the number of all visits and SSD-related visits over the 180 days prior
to the index diagnosis:
```{r}
load(paste0(sim_out_path,"report_data/trends_output.RData"))
load(paste0(sim_out_path,"trends/fit_trends.RData"))

trends_ssd <- ssd_vis_count_fitted %>% 
  rename(tot_miss=num_miss) %>% 
  unnest(counts) %>% 
  mutate(model_label = paste0(model," (CP = ",cp," days)"))

mse_res_ssd <- trends_ssd %>%
  filter(is.na(num_miss)) %>% 
  group_by(model_label) %>% 
  summarise(rmse = sqrt(mean((pred-n)^2))) %>% 
  mutate(label = paste("RMSE: ", round(rmse,2)))

trends_all <- all_vis_count_fitted %>% 
  rename(tot_miss=num_miss) %>% 
  unnest(counts) %>% 
  mutate(model_label = paste0(model," (CP = ",cp," days)"))

mse_res_all <- trends_all %>%
  filter(is.na(num_miss)) %>% 
  group_by(model_label) %>% 
  summarise(rmse = sqrt(mean((pred-n)^2))) %>% 
  mutate(label = paste("RMSE: ", round(rmse,2)))

bind_rows(trends_ssd %>% 
            filter(cp ==7, model=="exponential") %>% 
            select(period,n) %>% 
            mutate(group = "SSD Visits"),
          trends_all %>% 
            filter(cp ==7, model=="exponential") %>% 
            select(period,n) %>% 
            mutate(group = "All Visits")) %>% 
  ggplot(aes(period,n)) +
  geom_line() +
  scale_x_reverse() +
  facet_wrap(~group, scale = "free_y") +
  ylab("Number of visits") +
  xlab("Days before index sepsis diagnosis") +
  theme_bw() 
  


```


# Expected visit trends

We compared 4 different approaches to estimate the expected number of visits prior 
to the index diagnosis:

1) Exponential Trend with a 14 day change-point
2) Exponential Trend with a 7 day change-point
3) Cubic Trend with a 14 day change-point
4) Cubic Trend with a 7 day change-point

Each of these models was fit to the SSD-related visits and all visits

### SSD Visits

```{r}


```

The following plot depicts the number of SSD visits each day before the index
sepsis diagnosis
```{r}

y_pos <- .9*max(trends_ssd$n)
x_pos <- .8*180


trends_ssd %>%
  ggplot(aes(period,n)) +
  geom_line() +
  scale_x_reverse() +
  geom_line(aes(y = pred), color = "red") +
  facet_wrap(~model_label) +
  geom_vline(aes(xintercept = cp), linetype =2) +
  theme_bw() +
  geom_text(data = mse_res_ssd,
            mapping = aes(x = x_pos, y = y_pos, label = label)) +
  ylab("Number of SSD visits") +
  xlab("Days before index sepsis diagnosis")
```

### All Visits
The following plot depicts the number of all visits each day before the index
sepsis diagnosis
```{r}

y_pos <- .9*max(trends_all$n)


trends_all %>%
  ggplot(aes(period,n)) +
  geom_line() +
  scale_x_reverse() +
  geom_line(aes(y = pred), color = "red") +
  facet_wrap(~model_label) +
  geom_vline(aes(xintercept = cp), linetype =2) +
  theme_bw() +
  geom_text(data = mse_res_all,
            mapping = aes(x = x_pos, y = y_pos, label = label)) +
  ylab("Number of visits (any reason)") +
  xlab("Days before index sepsis diagnosis")
```

## Summary
The following table summarize the model fit and implied number of missed opportunities
across models, change-points, and visit types.

```{r}
trends_out$model_comparisons_table %>% 
  kableExtra::kable() %>% 
  kableExtra::kable_styling(full_width = F)

```


# Results using SSD visits

### Overview

The following table summarizes the overall results for the different models that
were run in terms of the number and percent of patients that were missed, duration
of diagnostic delays and the number of missed opportunities that patients experienced:
```{r}
load(paste0(sim_out_path, "report_data/agg_stats.RData"))

better_labels <- tibble(measure = c("pct_pat","n_pat","mean_dur","median_dur","mean_n_miss","median_n_miss"),
                        Measure = c("Percent of patients w/ miss", "Number of patients w/ miss","Mean duration of delay", "Median duration of delay",
                                    "Mean # of misses (per patient w/ miss)", "Median # of misses (per patient w/ miss)"))

tmp1 <- agg_stats$exponential_14$agg_stats_ssd$main_stats %>% 
  inner_join(better_labels) %>% 
  select(Measure, `Exponential 14-day CP`=measure_out)

tmp2 <- agg_stats$exponential_7$agg_stats_ssd$main_stats %>% 
  inner_join(better_labels) %>% 
  select(Measure, `Exponential 7-day CP`=measure_out)

tmp3 <- agg_stats$cubic_7$agg_stats_ssd$main_stats %>% 
  inner_join(better_labels) %>% 
  select(Measure, `Cubic 7-day CP`=measure_out)

inner_join(tmp1,tmp2,by = join_by(Measure)) %>% 
  inner_join(tmp3,by = join_by(Measure)) %>%
  filter(Measure !="Number of patients w/ miss") %>% 
  kableExtra::kable() %>% 
  kableExtra::kable_styling(full_width = F) 

```


### Primary Model - Exponential trend w/ 14-day change-point

The following table presents the aggregated summary statistics
```{r}
agg_stats$exponential_14$agg_stats_ssd$main_stats %>% 
  inner_join(better_labels) %>% 
  select(Measure, `Estimate (95% CI)`=measure_out) %>% 
  kableExtra::kable() %>% 
  kableExtra::kable_styling(full_width = F)

```

The following table presents the distribution of delay duration:
```{r}
agg_stats$exponential_14$agg_stats_ssd$duration_bins %>% 
  mutate(Duration = paste0(">= ", duration_bin," days")) %>% 
  rename(`Number of patients`=n, `Percent of all patients`=pct_all,
         `Percent of patients w/ miss` = pct_miss) %>% 
  select(-duration_bin) %>% 
  select(Duration, everything()) %>% 
  kableExtra::kable() %>% 
  kableExtra::kable_styling(full_width = F)
```

The following table presents the distribution of the number of missed opportunities 
that individual patients experienced:
```{r}
agg_stats$exponential_14$agg_stats_ssd$miss_bins %>% 
  mutate(`Number of misses` = paste0(">= ", miss_bin)) %>% 
  rename(`Number of patients`=n, `Percent of all patients`=pct_all,
         `Percent of patients w/ miss` = pct_miss) %>% 
  select(-miss_bin) %>% 
  select(`Number of misses`, everything()) %>% 
  kableExtra::kable() %>% 
  kableExtra::kable_styling(full_width = F)
```


### Sensitivity Analysis - Exponential trend w/ 7-day change-point

The following table presents the aggregated summary statistics
```{r}
agg_stats$exponential_7$agg_stats_ssd$main_stats %>% 
  inner_join(better_labels) %>% 
  select(Measure, `Estimate (95% CI)`=measure_out) %>% 
  kableExtra::kable() %>% 
  kableExtra::kable_styling(full_width = F)

```

The following table presents the distribution of delay duration:
```{r}
agg_stats$exponential_7$agg_stats_ssd$duration_bins %>% 
  filter(duration_bin<=7) %>% 
  mutate(Duration = paste0(">= ", duration_bin," days")) %>% 
  rename(`Number of patients`=n, `Percent of all patients`=pct_all,
         `Percent of patients w/ miss` = pct_miss) %>% 
  select(-duration_bin) %>% 
  select(Duration, everything()) %>% 
  kableExtra::kable() %>% 
  kableExtra::kable_styling(full_width = F)
```

The following table presents the distribution of the number of missed opportunities 
that individual patients experienced:
```{r}
agg_stats$exponential_7$agg_stats_ssd$miss_bins %>% 
  mutate(`Number of misses` = paste0(">= ", miss_bin)) %>% 
  rename(`Number of patients`=n, `Percent of all patients`=pct_all,
         `Percent of patients w/ miss` = pct_miss) %>% 
  select(-miss_bin) %>% 
  select(`Number of misses`, everything()) %>% 
  kableExtra::kable() %>% 
  kableExtra::kable_styling(full_width = F)
```

### Sensitivity Analysis - Cubic trend w/ 14-day change-point

### Sensitivity Analysis - Cubic trend w/ 7-day change-point

The following table presents the aggregated summary statistics
```{r}
agg_stats$cubic_7$agg_stats_ssd$main_stats %>% 
  inner_join(better_labels) %>% 
  select(Measure, `Estimate (95% CI)`=measure_out) %>% 
  kableExtra::kable() %>% 
  kableExtra::kable_styling(full_width = F)

```

The following table presents the distribution of delay duration:
```{r}
agg_stats$cubic_7$agg_stats_ssd$duration_bins %>% 
  filter(duration_bin<=7) %>% 
  mutate(Duration = paste0(">= ", duration_bin," days")) %>% 
  rename(`Number of patients`=n, `Percent of all patients`=pct_all,
         `Percent of patients w/ miss` = pct_miss) %>% 
  select(-duration_bin) %>% 
  select(Duration, everything()) %>% 
  kableExtra::kable() %>% 
  kableExtra::kable_styling(full_width = F)
```

The following table presents the distribution of the number of missed opportunities 
that individual patients experienced:
```{r}
agg_stats$cubic_7$agg_stats_ssd$miss_bins %>% 
  mutate(`Number of misses` = paste0(">= ", miss_bin)) %>% 
  rename(`Number of patients`=n, `Percent of all patients`=pct_all,
         `Percent of patients w/ miss` = pct_miss) %>% 
  select(-miss_bin) %>% 
  select(`Number of misses`, everything()) %>% 
  kableExtra::kable() %>% 
  kableExtra::kable_styling(full_width = F)
```


# Results using All visits

### Primary Model - Exponential trend w/ 14-day change-point

The following table presents the aggregated summary statistics
```{r}
agg_stats$exponential_14$agg_stats_all$main_stats %>% 
  inner_join(better_labels) %>% 
  select(Measure, `Estimate (95% CI)`=measure_out) %>% 
  kableExtra::kable() %>% 
  kableExtra::kable_styling(full_width = F)

```

The following table presents the distribution of delay duration:
```{r}
agg_stats$exponential_14$agg_stats_all$duration_bins %>% 
  mutate(Duration = paste0(">= ", duration_bin," days")) %>% 
  rename(`Number of patients`=n, `Percent of all patients`=pct_all,
         `Percent of patients w/ miss` = pct_miss) %>% 
  select(-duration_bin) %>% 
  select(Duration, everything()) %>% 
  kableExtra::kable() %>% 
  kableExtra::kable_styling(full_width = F)
```

The following table presents the distribution of the number of missed opportunities 
that individual patients experienced:
```{r}
agg_stats$exponential_14$agg_stats_all$miss_bins %>% 
  mutate(`Number of misses` = paste0(">= ", miss_bin)) %>% 
  rename(`Number of patients`=n, `Percent of all patients`=pct_all,
         `Percent of patients w/ miss` = pct_miss) %>% 
  select(-miss_bin) %>% 
  select(`Number of misses`, everything()) %>% 
  kableExtra::kable() %>% 
  kableExtra::kable_styling(full_width = F)
```

### Sensitivity Analysis - Exponential trend w/ 7-day change-point

The following table presents the aggregated summary statistics
```{r}
agg_stats$exponential_7$agg_stats_all$main_stats %>% 
  inner_join(better_labels) %>% 
  select(Measure, `Estimate (95% CI)`=measure_out) %>% 
  kableExtra::kable() %>% 
  kableExtra::kable_styling(full_width = F)

```

The following table presents the distribution of delay duration:
```{r}
agg_stats$exponential_7$agg_stats_all$duration_bins %>% 
  filter(duration_bin<=7) %>% 
  mutate(Duration = paste0(">= ", duration_bin," days")) %>% 
  rename(`Number of patients`=n, `Percent of all patients`=pct_all,
         `Percent of patients w/ miss` = pct_miss) %>% 
  select(-duration_bin) %>% 
  select(Duration, everything()) %>% 
  kableExtra::kable() %>% 
  kableExtra::kable_styling(full_width = F)
```

The following table presents the distribution of the number of missed opportunities 
that individual patients experienced:
```{r}
agg_stats$exponential_7$agg_stats_all$miss_bins %>% 
  mutate(`Number of misses` = paste0(">= ", miss_bin)) %>% 
  rename(`Number of patients`=n, `Percent of all patients`=pct_all,
         `Percent of patients w/ miss` = pct_miss) %>% 
  select(-miss_bin) %>% 
  select(`Number of misses`, everything()) %>% 
  kableExtra::kable() %>% 
  kableExtra::kable_styling(full_width = F)
```

### Sensitivity Analysis - Cubic trend w/ 14-day change-point

### Sensitivity Analysis - Cubic trend w/ 7-day change-point
The following table presents the aggregated summary statistics
```{r}
agg_stats$cubic_7$agg_stats_all$main_stats %>% 
  inner_join(better_labels) %>% 
  select(Measure, `Estimate (95% CI)`=measure_out) %>% 
  kableExtra::kable() %>% 
  kableExtra::kable_styling(full_width = F)

```

The following table presents the distribution of delay duration:
```{r}
agg_stats$cubic_7$agg_stats_all$duration_bins %>% 
  filter(duration_bin<=7) %>% 
  mutate(Duration = paste0(">= ", duration_bin," days")) %>% 
  rename(`Number of patients`=n, `Percent of all patients`=pct_all,
         `Percent of patients w/ miss` = pct_miss) %>% 
  select(-duration_bin) %>% 
  select(Duration, everything()) %>% 
  kableExtra::kable() %>% 
  kableExtra::kable_styling(full_width = F)
```

The following table presents the distribution of the number of missed opportunities 
that individual patients experienced:
```{r}
agg_stats$cubic_7$agg_stats_all$miss_bins %>% 
  mutate(`Number of misses` = paste0(">= ", miss_bin)) %>% 
  rename(`Number of patients`=n, `Percent of all patients`=pct_all,
         `Percent of patients w/ miss` = pct_miss) %>% 
  select(-miss_bin) %>% 
  select(`Number of misses`, everything()) %>% 
  kableExtra::kable() %>% 
  kableExtra::kable_styling(full_width = F)
```