---
title: "Opportunity Window Report"
author: ""
date: "`r Sys.Date()`"
params:
  cond:
    value: x
output: html_document
editor_options: 
  markdown: 
    wrap: 72
---

```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = TRUE)
library(tidyverse)
library(kableExtra)

# This needs to be passed as an argument
condition <- params$cond

load("/Shared/AML/params/delay_any_params.RData")
# load("/Volumes/AML/params/delay_any_params.RData")
delay_params <- delay_any_params[[condition]]

# If change-point bounds are missing replace with default range from 10 to 100
if (is.na(delay_params$cp_lower) | is.na(delay_params$cp_upper)){
  cp_lower <- 10
  cp_upper <- 100
} else {
  cp_lower <- delay_params$cp_lower
  cp_upper <- delay_params$cp_upper
}

# Extract Condition Name
condition_name <- codeBuildr::avail_disease_codes() %>% 
  filter(name==condition) %>% 
  .$description


load(paste0("/Shared/Statepi_Diagnosis/prelim_results/",condition,"/change_point_results/cp_boot_eval_res.RData"))
# load(paste0("/Volumes/Statepi_Diagnosis/prelim_results/",condition,"/change_point_results/cp_boot_eval_res.RData"))
```

This report summarizes the results of the bootstrapping change-point
approach to select the diagnostic opportunity window for
**`r condition_name`**. For this report we analyzed opportunity windows
ranging from **`r cp_lower`** to **`r cp_upper`** days prior to the
index diagnosis.

The following approach was used for this report. For a given range of
opportunity bound, *OB*, (e.g., 50 days before diagnosis) do the
following:

1.  Generate 100 bootstrapped samples, by selecting individual patients
    with replacement. For each sample, compute the number of visits (any
    or SSD) each day before diagnosis.

2.  For a given bootstrap and opportunity bound, *OB*, perform the
    following:

    1.  **Estimate Expected Trends** - Estimate linear, quadratic, and
        cubic trends over the control window from
        `r delay_params$upper_bound` to *OB* days before diagnosis.

    2.  Extrapolate this trend forward into the implied opportunity
        window, from *OB* to 1 day before diagnosis.

    3.  **Estimate Excess Trends** - Compute the residuals during the
        opportunity window (these are the "excess" visits) as the
        difference between the observed values and the expected trend
        from step 2. Use a LOESS model to fit this *excess* trend.

    4.  Compute the final fitted trend as the sum of the expected and
        excess trends.

3.  Using the final estimated trend, compute in-sample and out-of-sample
    performance defined by the following:

    -   **In-sample** - Compare the observed and fitted values within
        the bootstrapped sample used to fit the model

    -   **Aggregate Out-of-sample** - Compare the observed values from the
        aggregated (non-bootstrapped) patient data to the fitted values
        from the bootstrap samples.

    -   **K-fold (99-fold) Out-of-sample** - Compare the observed
        values from the other bootstrapped sample to the fitted values
        from a given bootstrap sample.

4.  Repeat steps 2-3 across the range of opportunity bounds from
    **`r cp_lower`** to **`r cp_upper`** days before diagnosis and
    bootstrap samples.

5.  Aggregate performance metrics across bootstrap samples.

## Visits before `r condition_name`

The following figure depicts the number of patients with any visit or an
SSD-related visit each day prior to diagnosis:

```{r, echo = FALSE}
visit_counts %>% 
  mutate(label = paste0(code_set," Visits")) %>% 
  ggplot(aes(-days_since_index,n)) +
  geom_point() +
  scale_x_reverse() +
  facet_wrap(~label, scale = "free_y") +
  theme_bw() +
  xlab("Days Before Diagnosis") +
  ylab("Number of Patients")

```

## SSD Visits

This section summarizes results using counts of SSD-related visits.

The following figure depicts the in-sample and out-of-sample performance
(MSE) of various bounds on the opportunity window and different trends.

```{r, echo = FALSE}
inner_join(in_sample_mse_ssd,out_of_sample_mse_ssd,by = join_by(cp, model)) %>%
  inner_join(select(kfold_mse_ssd,model,cp,out_mse_other_boot=mean_mse),by = join_by(cp, model)) %>% 
  gather(key = key, value = value, -model, -cp)  %>% 
  mutate(label = ifelse(key == "in_mse", "In-Sample",
                        ifelse(key=="out_mse","Out-of-Sample (Aggregate)","Out-of-Sample (K-fold)"))) %>% 
  inner_join(tibble(model=c("linear","quad","cube"),
                    model_lab = c("Linear", "Quadratic", "Cubic")),
             by = join_by(model)) %>% 
  ggplot(aes(cp,value,color = model_lab)) +
  geom_line() +
  facet_wrap(~label,scale = "free_y") +
  theme_bw() +
  ylab("MSE") +
  xlab("Opportunity Window Upper Bound") +
  theme(legend.title = element_blank(),
        legend.position = "bottom")
```

The following table depicts the top 10 specifications based on either aggregate or
k-fold out-of-sample performance:

```{r, echo = FALSE}
tab1 <- out_of_sample_mse_ssd %>% 
  ungroup() %>% 
  arrange(out_mse) %>% 
  mutate(cp = -cp) %>% 
  inner_join(tibble(model=c("linear","quad","cube"),
                    model_lab = c("Linear", "Quadratic", "Cubic")),
             by = join_by(model)) %>% 
  select(cp,model_lab,out_mse) %>% 
  rename(`Bound (Days)`=cp,Model=model_lab,MSE=out_mse) %>% 
  slice(1:10) %>% 
  mutate(rank = row_number()) %>% 
  mutate(MSE = round(MSE,2)) %>% 
  select(rank,everything())

tab2 <- kfold_mse_ssd %>% 
  select(model,cp,out_mse=mean_mse) %>% 
  arrange(out_mse) %>% 
  mutate(cp = -cp) %>% 
  inner_join(tibble(model=c("linear","quad","cube"),
                    model_lab = c("Linear", "Quadratic", "Cubic")),
             by = join_by(model)) %>% 
  select(cp,model_lab,out_mse) %>% 
  mutate(out_mse = round(out_mse,2)) %>% 
  rename(`Bound (Days)`=cp,Model=model_lab,MSE=out_mse) %>% 
  slice(1:10)

cbind(tab1,tab2) %>% 
  kable(align = 'c', booktabs = TRUE) %>% 
  kable_styling(full_width = F) %>% 
  add_header_above(c(" " = 1, "Aggregate Out-of-Sample" = 3, "K-Fold Out-of-Sample" = 3))
```

The following figure depicts the observed and expected trend for the top
4 models based on **aggregate out-of-sample** performance:

```{r, echo = FALSE, message=FALSE,warning=FALSE,out.width="100%"}
out_of_sample_mse_ssd %>% 
  ungroup() %>% 
  arrange(out_mse) %>% 
  slice(1:4) %>% 
  inner_join(tibble(model=c("linear","quad","cube"),
                    model_lab = c("Linear", "Quadratic", "Cubic")),
             by = join_by(model)) %>% 
  mutate(label = paste0(model_lab,": ",-cp, " days")) %>% 
  inner_join(cp_fits_ssd,by = join_by(cp, model)) %>% 
  ggplot(aes(-days_since_index,n)) +
  geom_point(size = 0.8) +
  geom_line(aes(y=combined), color = "blue", size = 0.7) +
  geom_line(aes(y=expected), color = "red", size = 0.7) +
  geom_vline(aes(xintercept = -cp), linetype = 2) +
  facet_wrap(~label) +
  scale_x_reverse() +
  theme_bw() +
  ylab("Number of Patients") +
  xlab("Days Before Diagnosis") 

```

The following figure depicts the observed and expected trend for the top
4 models based on **99-fold out-of-sample** performance:

```{r, echo = FALSE, message=FALSE,warning=FALSE,out.width="100%"}
kfold_mse_ssd %>% 
  arrange(mean_mse) %>% 
  slice(1:4) %>% 
  inner_join(tibble(model=c("linear","quad","cube"),
                    model_lab = c("Linear", "Quadratic", "Cubic")),
             by = join_by(model)) %>% 
  mutate(label = paste0(model_lab,": ",-cp, " days")) %>% 
  inner_join(cp_fits_ssd,by = join_by(cp, model)) %>% 
  ggplot(aes(-days_since_index,n)) +
  geom_point(size = 0.8) +
  geom_line(aes(y=combined), color = "blue", size = 0.7) +
  geom_line(aes(y=expected), color = "red", size = 0.7) +
  geom_vline(aes(xintercept = -cp), linetype = 2) +
  facet_wrap(~label) +
  scale_x_reverse() +
  theme_bw() +
  ylab("Number of Patients") +
  xlab("Days Before Diagnosis") 

```

The following table depicts the 10 best models for each trend, based on **aggregate
out-of-sample** performance:

```{r, echo = FALSE}
tmp1 <- out_of_sample_mse_ssd %>% 
  ungroup() %>% 
  group_by(model) %>% 
  arrange(model,out_mse) %>% 
  slice(1:10) %>% 
  mutate(rank = 1:10,
         cp = -cp) %>% 
  ungroup()

tmp_lin <- filter(tmp1,model=="linear") %>% 
  select(Rank = rank, Bound = cp,MSE = out_mse) %>% 
  mutate(MSE = round(MSE,2)) %>% 
  as.matrix()

tmp_quad <- filter(tmp1,model=="quad") %>% 
  select(Bound = cp,MSE = out_mse) %>% 
  mutate(MSE = round(MSE,2)) %>% 
  as.matrix()

tmp_cube <- filter(tmp1,model=="cube") %>% 
  select(Bound = cp,MSE = out_mse) %>% 
  mutate(MSE = round(MSE,2)) %>% 
  as.matrix()

cbind(tmp_lin,tmp_quad,tmp_cube) %>% 
  kable(align = 'c', booktabs = TRUE) %>% 
  kable_styling(full_width = F) %>% 
  add_header_above(c(" " = 1, "Linear" = 2, "Quadratic" = 2, "Cubic" = 2))

```

The following table depicts the 10 best models for each trend, based on **99-fold
out-of-sample** performance:

```{r, echo = FALSE}
tmp2 <- kfold_mse_ssd %>% 
  select(model,cp,out_mse = mean_mse) %>% 
  group_by(model) %>% 
  arrange(model,out_mse) %>% 
  slice(1:10) %>% 
  mutate(rank = 1:10,
         cp = -cp) %>% 
  ungroup()

tmp_lin <- filter(tmp2,model=="linear") %>% 
  select(Rank = rank, Bound = cp,MSE = out_mse) %>% 
  mutate(MSE = round(MSE,2)) %>% 
  as.matrix()

tmp_quad <- filter(tmp2,model=="quad") %>% 
  select(Bound = cp,MSE = out_mse) %>% 
  mutate(MSE = round(MSE,2)) %>% 
  as.matrix()

tmp_cube <- filter(tmp2,model=="cube") %>% 
  select(Bound = cp,MSE = out_mse) %>% 
  mutate(MSE = round(MSE,2)) %>% 
  as.matrix()

cbind(tmp_lin,tmp_quad,tmp_cube) %>% 
  kable(align = 'c', booktabs = TRUE) %>% 
  kable_styling(full_width = F) %>% 
  add_header_above(c(" " = 1, "Linear" = 2, "Quadratic" = 2, "Cubic" = 2))

```

### Linear Models

The following figure depicts the top 4 performing linear models based on **aggregate
out-of-sample** MSE:

```{r, echo = FALSE, out.width="100%"}
filter(tmp1,model=="linear") %>% 
  filter(rank<=4) %>% 
  mutate(cp = -cp) %>% 
  inner_join(cp_fits_ssd, by = join_by(cp, model)) %>%
  mutate(label = paste0("Linear: ",-cp," days - MSE: ",round(out_mse,2))) %>% 
  ggplot(aes(-days_since_index,n)) +
  geom_point(size = 0.8) +
  geom_line(aes(y=combined), color = "blue", size = 0.7) +
  geom_line(aes(y=expected), color = "red", size = 0.7) +
  geom_vline(aes(xintercept = -cp), linetype = 2) +
  facet_wrap(~label) +
  scale_x_reverse() +
  theme_bw() +
  ylab("Number of Patients") +
  xlab("Days Before Diagnosis")
```

The following figure depicts the top 4 performing linear models based on **99-fold
out-of-sample** MSE:

```{r, echo = FALSE, out.width="100%"}
filter(tmp2,model=="linear") %>% 
  filter(rank<=4) %>% 
  mutate(cp = -cp) %>% 
  inner_join(cp_fits_ssd, by = join_by(cp, model)) %>%
  mutate(label = paste0("Linear: ",-cp," days - MSE: ",round(out_mse,2))) %>% 
  ggplot(aes(-days_since_index,n)) +
  geom_point(size = 0.8) +
  geom_line(aes(y=combined), color = "blue", size = 0.7) +
  geom_line(aes(y=expected), color = "red", size = 0.7) +
  geom_vline(aes(xintercept = -cp), linetype = 2) +
  facet_wrap(~label) +
  scale_x_reverse() +
  theme_bw() +
  ylab("Number of Patients") +
  xlab("Days Before Diagnosis")

```

### Quadratic Models

The following figure depicts the top 4 performing quadratic models based
on **aggregate out-of-sample** MSE:

```{r, echo = FALSE, out.width="100%"}
filter(tmp1,model=="quad") %>% 
  filter(rank<=4) %>% 
  mutate(cp = -cp) %>% 
  inner_join(cp_fits_ssd, by = join_by(cp, model)) %>%
  mutate(label = paste0("Quadratic: ",-cp," days - MSE: ",round(out_mse,2))) %>% 
  ggplot(aes(-days_since_index,n)) +
  geom_point(size = 0.8) +
  geom_line(aes(y=combined), color = "blue", size = 0.7) +
  geom_line(aes(y=expected), color = "red", size = 0.7) +
  geom_vline(aes(xintercept = -cp), linetype = 2) +
  facet_wrap(~label) +
  scale_x_reverse() +
  theme_bw() +
  ylab("Number of Patients") +
  xlab("Days Before Diagnosis")
```

The following figure depicts the top 4 performing quadratic models based
on **99-fold out-of-sample** MSE:

```{r, echo = FALSE, out.width="100%"}
filter(tmp2,model=="quad") %>% 
  filter(rank<=4) %>% 
  mutate(cp = -cp) %>% 
  inner_join(cp_fits_ssd, by = join_by(cp, model)) %>%
  mutate(label = paste0("Quadratic: ",-cp," days - MSE: ",round(out_mse,2))) %>% 
  ggplot(aes(-days_since_index,n)) +
  geom_point(size = 0.8) +
  geom_line(aes(y=combined), color = "blue", size = 0.7) +
  geom_line(aes(y=expected), color = "red", size = 0.7) +
  geom_vline(aes(xintercept = -cp), linetype = 2) +
  facet_wrap(~label) +
  scale_x_reverse() +
  theme_bw() +
  ylab("Number of Patients") +
  xlab("Days Before Diagnosis")
```

### Cubic Models

The following figure depicts the top 4 performing cubic models based on
**aggregate out-of-sample** MSE:

```{r, echo = FALSE, out.width="100%"}
filter(tmp1,model=="cube") %>% 
  filter(rank<=4) %>% 
  mutate(cp = -cp) %>% 
  inner_join(cp_fits_ssd, by = join_by(cp, model)) %>%
  mutate(label = paste0("Cubic: ",-cp," days - MSE: ",round(out_mse,2))) %>% 
  ggplot(aes(-days_since_index,n)) +
  geom_point(size = 0.8) +
  geom_line(aes(y=combined), color = "blue", size = 0.7) +
  geom_line(aes(y=expected), color = "red", size = 0.7) +
  geom_vline(aes(xintercept = -cp), linetype = 2) +
  facet_wrap(~label) +
  scale_x_reverse() +
  theme_bw() +
  ylab("Number of Patients") +
  xlab("Days Before Diagnosis")
```

The following figure depicts the top 4 performing cubic models based on
**99-fold out-of-sample** MSE:

```{r, echo = FALSE, out.width="100%"}
filter(tmp2,model=="cube") %>% 
  filter(rank<=4) %>% 
  mutate(cp = -cp) %>% 
  inner_join(cp_fits_ssd, by = join_by(cp, model)) %>%
  mutate(label = paste0("Cubic: ",-cp," days - MSE: ",round(out_mse,2))) %>% 
  ggplot(aes(-days_since_index,n)) +
  geom_point(size = 0.8) +
  geom_line(aes(y=combined), color = "blue", size = 0.7) +
  geom_line(aes(y=expected), color = "red", size = 0.7) +
  geom_vline(aes(xintercept = -cp), linetype = 2) +
  facet_wrap(~label) +
  scale_x_reverse() +
  theme_bw() +
  ylab("Number of Patients") +
  xlab("Days Before Diagnosis")
```

## All Visits

This section summarizes results using counts of all visits.

The following figure depicts the in-sample and out-of-sample performance
of various bounds on the opportunity window and different trends.

```{r, echo = FALSE}
inner_join(in_sample_mse_all,out_of_sample_mse_all,by = join_by(cp, model)) %>%
  gather(key = key, value = value, -model, -cp)  %>% 
  mutate(label = ifelse(key == "in_mse", "In-Sample MSE", "Out-of-Sample MSE")) %>% 
  inner_join(tibble(model=c("linear","quad","cube"),
                    model_lab = c("Linear", "Quadratic", "Cubic")),
             by = join_by(model)) %>% 
  ggplot(aes(cp,value,color = model_lab)) +
  geom_line() +
  facet_wrap(~label,scale = "free_y") +
  theme_bw() +
  ylab("MSE") +
  xlab("Opportunity Window Upper Bound") +
  theme(legend.title = element_blank(),
        legend.position = "bottom")
```

The following table depicts the top 10 specifications based on both aggregate and
k-fold out-of-sample performance:

```{r, echo = FALSE}
tab1 <- out_of_sample_mse_all %>% 
  ungroup() %>% 
  arrange(out_mse) %>% 
  mutate(cp = -cp) %>% 
  inner_join(tibble(model=c("linear","quad","cube"),
                    model_lab = c("Linear", "Quadratic", "Cubic")),
             by = join_by(model)) %>% 
  select(cp,model_lab,out_mse) %>% 
  rename(`Bound (Days)`=cp,Model=model_lab,MSE=out_mse) %>% 
  slice(1:10) %>% 
  mutate(rank = row_number()) %>% 
  mutate(MSE = round(MSE,2)) %>% 
  select(rank,everything())

tab2 <- kfold_mse_all %>% 
  select(model,cp,out_mse=mean_mse) %>% 
  arrange(out_mse) %>% 
  mutate(cp = -cp) %>% 
  inner_join(tibble(model=c("linear","quad","cube"),
                    model_lab = c("Linear", "Quadratic", "Cubic")),
             by = join_by(model)) %>% 
  select(cp,model_lab,out_mse) %>% 
  mutate(out_mse = round(out_mse,2)) %>% 
  rename(`Bound (Days)`=cp,Model=model_lab,MSE=out_mse) %>% 
  slice(1:10)

cbind(tab1,tab2) %>% 
  kable(align = 'c', booktabs = TRUE) %>% 
  kable_styling(full_width = F) %>% 
  add_header_above(c(" " = 1, "Aggregate Out-of-Sample" = 3, "K-Fold Out-of-Sample" = 3))
```

The following figure depicts the observed and expected trend for the top
4 models based on **aggregate out-of-sample** performance:

```{r, echo = FALSE, message=FALSE,warning=FALSE,out.width="100%"}
out_of_sample_mse_all %>% 
  ungroup() %>% 
  arrange(out_mse) %>% 
  slice(1:4) %>% 
  inner_join(tibble(model=c("linear","quad","cube"),
                    model_lab = c("Linear", "Quadratic", "Cubic")),
             by = join_by(model)) %>% 
  mutate(label = paste0(model_lab,": ",-cp, " days")) %>% 
  inner_join(cp_fits_all,by = join_by(cp, model)) %>% 
  ggplot(aes(-days_since_index,n)) +
  geom_point(size = 0.8) +
  geom_line(aes(y=combined), color = "blue", size = 0.7) +
  geom_line(aes(y=expected), color = "red", size = 0.7) +
  geom_vline(aes(xintercept = -cp), linetype = 2) +
  facet_wrap(~label) +
  scale_x_reverse() +
  theme_bw() +
  ylab("Number of Patients") +
  xlab("Days Before Diagnosis") 

```

The following figure depicts the observed and expected trend for the top
4 models based on **k-fold out-of-sample** performance:

```{r, echo = FALSE, message=FALSE,warning=FALSE,out.width="100%"}
kfold_mse_all %>% 
  arrange(mean_mse) %>% 
  slice(1:4) %>% 
  inner_join(tibble(model=c("linear","quad","cube"),
                    model_lab = c("Linear", "Quadratic", "Cubic")),
             by = join_by(model)) %>% 
  mutate(label = paste0(model_lab,": ",-cp, " days")) %>% 
  inner_join(cp_fits_all,by = join_by(cp, model)) %>% 
  ggplot(aes(-days_since_index,n)) +
  geom_point(size = 0.8) +
  geom_line(aes(y=combined), color = "blue", size = 0.7) +
  geom_line(aes(y=expected), color = "red", size = 0.7) +
  geom_vline(aes(xintercept = -cp), linetype = 2) +
  facet_wrap(~label) +
  scale_x_reverse() +
  theme_bw() +
  ylab("Number of Patients") +
  xlab("Days Before Diagnosis") 

```



The following table depicts the 10 best models for each trend, based on **aggregate
out-of-sample** performance:

```{r, echo = FALSE}
tmp <- out_of_sample_mse_all %>% 
  ungroup() %>% 
  group_by(model) %>% 
  arrange(model,out_mse) %>% 
  slice(1:10) %>% 
  mutate(rank = 1:10,
         cp = -cp) %>% 
  ungroup()

tmp_lin <- filter(tmp,model=="linear") %>% 
  select(Rank = rank, Bound = cp,MSE = out_mse) %>% 
  mutate(MSE = round(MSE,2)) %>% 
  as.matrix()

tmp_quad <- filter(tmp,model=="quad") %>% 
  select(Bound = cp,MSE = out_mse) %>% 
  mutate(MSE = round(MSE,2)) %>% 
  as.matrix()

tmp_cube <- filter(tmp,model=="cube") %>% 
  select(Bound = cp,MSE = out_mse) %>% 
  mutate(MSE = round(MSE,2)) %>% 
  as.matrix()

cbind(tmp_lin,tmp_quad,tmp_cube) %>% 
  kable(align = 'c', booktabs = TRUE) %>% 
  kable_styling(full_width = F) %>% 
  add_header_above(c(" " = 1, "Linear" = 2, "Quadratic" = 2, "Cubic" = 2))

```

The following table depicts the 10 best models for each trend, based on **99-fold
out-of-sample** performance:

```{r, echo = FALSE}
tmp <- kfold_mse_all %>% 
  select(model,cp,out_mse = mean_mse) %>% 
  group_by(model) %>% 
  arrange(model,out_mse) %>% 
  slice(1:10) %>% 
  mutate(rank = 1:10,
         cp = -cp) %>% 
  ungroup()

tmp_lin <- filter(tmp,model=="linear") %>% 
  select(Rank = rank, Bound = cp,MSE = out_mse) %>% 
  mutate(MSE = round(MSE,2)) %>% 
  as.matrix()

tmp_quad <- filter(tmp,model=="quad") %>% 
  select(Bound = cp,MSE = out_mse) %>% 
  mutate(MSE = round(MSE,2)) %>% 
  as.matrix()

tmp_cube <- filter(tmp,model=="cube") %>% 
  select(Bound = cp,MSE = out_mse) %>% 
  mutate(MSE = round(MSE,2)) %>% 
  as.matrix()

cbind(tmp_lin,tmp_quad,tmp_cube) %>% 
  kable(align = 'c', booktabs = TRUE) %>% 
  kable_styling(full_width = F) %>% 
  add_header_above(c(" " = 1, "Linear" = 2, "Quadratic" = 2, "Cubic" = 2))

```


### Linear Models

The following figure depicts the top 4 performing linear models based on
out-of-sample MSE

```{r, echo = FALSE, out.width="100%"}
filter(tmp,model=="linear") %>% 
  filter(rank<=4) %>% 
  mutate(cp = -cp) %>% 
  inner_join(cp_fits_all, by = join_by(cp, model)) %>%
  mutate(label = paste0("Linear: ",-cp," days - MSE: ",round(out_mse,2))) %>% 
  ggplot(aes(-days_since_index,n)) +
  geom_point(size = 0.8) +
  geom_line(aes(y=combined), color = "blue", size = 0.7) +
  geom_line(aes(y=expected), color = "red", size = 0.7) +
  geom_vline(aes(xintercept = -cp), linetype = 2) +
  facet_wrap(~label) +
  scale_x_reverse() +
  theme_bw() +
  ylab("Number of Patients") +
  xlab("Days Before Diagnosis")
```

### Quadratic Models

The following figure depicts the top 4 performing quadratic models based
on out-of-sample MSE

```{r, echo = FALSE, out.width="100%"}
filter(tmp,model=="quad") %>% 
  filter(rank<=4) %>% 
  mutate(cp = -cp) %>% 
  inner_join(cp_fits_all, by = join_by(cp, model)) %>%
  mutate(label = paste0("Quadratic: ",-cp," days - MSE: ",round(out_mse,2))) %>% 
  ggplot(aes(-days_since_index,n)) +
  geom_point(size = 0.8) +
  geom_line(aes(y=combined), color = "blue", size = 0.7) +
  geom_line(aes(y=expected), color = "red", size = 0.7) +
  geom_vline(aes(xintercept = -cp), linetype = 2) +
  facet_wrap(~label) +
  scale_x_reverse() +
  theme_bw() +
  ylab("Number of Patients") +
  xlab("Days Before Diagnosis")
```

### Cubic Models

The following figure depicts the top 4 performing cubic models based on
out-of-sample MSE

```{r, echo = FALSE, out.width="100%"}
filter(tmp,model=="cube") %>% 
  filter(rank<=4) %>% 
  mutate(cp = -cp) %>% 
  inner_join(cp_fits_all, by = join_by(cp, model)) %>%
  mutate(label = paste0("Cubic: ",-cp," days - MSE: ",round(out_mse,2))) %>% 
  ggplot(aes(-days_since_index,n)) +
  geom_point(size = 0.8) +
  geom_line(aes(y=combined), color = "blue", size = 0.7) +
  geom_line(aes(y=expected), color = "red", size = 0.7) +
  geom_vline(aes(xintercept = -cp), linetype = 2) +
  facet_wrap(~label) +
  scale_x_reverse() +
  theme_bw() +
  ylab("Number of Patients") +
  xlab("Days Before Diagnosis")
```
