---
title: "test_opp_window_report"
author: "Aaron Miller"
date: "`r Sys.Date()`"
output: html_document
---

```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = TRUE)
library(tidyverse)
library(kableExtra)

# This needs to be passed as an argument
condition <- "dengue"

params <- list()
params$cond <- condition

# Extract Condition Name
condition_name <- codeBuildr::avail_disease_codes() %>% 
  filter(name==condition) %>% 
  .$description

in_path <- paste0("~/Data/Statepi_Diagnosis/prelim_results/",condition,"/change_point_results/")

load(paste0(in_path,"standard_cp_res.RData"))
load(paste0(in_path,"cp_boot_eval_res.RData"))
```

This document provides a summary of the change-point analysis for `r condition_name` (`r params$cond`).


# Visit Trends

```{r, echo = FALSE}

bind_rows(mutate(SSD_res_standard$count_data_ssd,group = "SSD Visits"),
          mutate(ALL_res_standard$count_data_all,group = "All Visits")) %>% 
  ggplot(aes(period,n)) +
  geom_point() +
  scale_x_reverse() +
  theme_bw() +
  xlab("Days Before Index Diagnosis") +
  ylab("Number of Patients") +
  facet_wrap(~group, scale = "free_y")

```

# Piecewise CP Approach
The following section summarizes change-point analysis for trends in the number 
of visits before diagnosis using the standard piecewise-modeling approach to find 
the change-point. Specifically, we evaluate 4 peicewise models with linear,
quadratic, cubic and exponential trends. The change-point is found by iterating 
over different change-points and selecting the best fitting model based on AIC.

### Summary of Optimal Models based on RMSE

The following table depicts the optimal change-point selected for each approach
based on RMSE.
```{r, echo = FALSE, message=FALSE}
tibble(label = c("Piecewise lm w/ periodicity",
                 "Piecewise quad w/ periodicity",
                 "Piecewise cubic w/ periodicity",
                 "Piecewise exp w/ periodicity",
                 "Piecewise lm",
                 "Piecewise quad",
                 "Piecewise cubic",
                 "Piecewise exp")) %>% 
  left_join(SSD_res_standard$ssd_res_out) %>% 
  select(label,`Change Point`=cp,`Pred. Bound CP` = pred_bound_cp,`CP # Miss ` = cp_n_miss,`PB CP # Miss` = pb_cp_n_miss) %>% 
  kableExtra::kable() %>% 
  kableExtra::kable_styling(full_width = F)
```

The following figure depicts the optimal change-point for each method with periodicity.
```{r, echo = FALSE,out.width="100%"}
SSD_res_standard$plot_periodicity 

```


The following figure depicts the optimal change-point for each method without periodicity.
```{r, echo = FALSE,out.width="100%"}
SSD_res_standard$plot_no_periodicity

```

### Summary of Model Performance Across Change-points

The following table summarizes RMSE and the implied number of missed opportunities
across each method for the different change-points evaluated
```{r, echo = FALSE, message = FALSE}
tmp_rmse <- SSD_res_standard$ssd_fits %>% 
  filter(periodicity) %>% 
  select(cp,model,rmse) %>% 
  mutate(rmse = round(rmse,3)) %>% 
  spread(key = model, value = rmse) %>% 
  select(cp,lm,quad,cubic,exp)

tmp_miss <- SSD_res_standard$ssd_fits %>% 
  filter(periodicity) %>% 
  select(cp,model,n_miss) %>% 
  mutate(n_miss = round(n_miss,0)) %>% 
  spread(key = model, value = n_miss) %>% 
  select(cp,lm,quad,cubic,exp)

tmp_lm <- inner_join(select(tmp_rmse,cp,RMSE = lm),
           select(tmp_miss,cp,`N Miss Visits` = lm)) %>%
  mutate(weeks = cp/7) %>% 
  select(weeks,days=cp,RMSE,`N Miss Visits`)

tmp_quad <- inner_join(select(tmp_rmse,cp,RMSE = quad),
                     select(tmp_miss,cp,`N Miss Visits` = quad)) %>% 
  select(-cp)

tmp_cube <- inner_join(select(tmp_rmse,cp,RMSE = cubic),
                     select(tmp_miss,cp,`N Miss Visits` = cubic)) %>% 
  select(-cp)

tmp_exp <- inner_join(select(tmp_rmse,cp,RMSE = exp),
                     select(tmp_miss,cp,`N Miss Visits` = exp)) %>% 
  select(-cp)

tmp <- cbind(tmp_lm,tmp_quad,tmp_cube,tmp_exp)

j1 <- which.min(tmp[,3])
tmp[j1,3] <- tmp[j1,3] %>% cell_spec(bold = TRUE)

j2 <- which.min(tmp[,5])
tmp[j2,5] <- tmp[j2,5] %>% cell_spec(bold = TRUE)

j3 <- which.min(tmp[,7])
tmp[j3,7] <- tmp[j3,7] %>% cell_spec(bold = TRUE)

j4 <- which.min(tmp[,9])
tmp[j4,9] <- tmp[j4,9] %>% cell_spec(bold = TRUE)

tmp %>% 
  kable(align = 'c', booktabs = TRUE,escape = FALSE) %>% 
  kable_styling(full_width = F) %>% 
  add_header_above(c("Change Point" = 2, "Linear" = 2, "Quadratic" = 2, "Cubic" = 2, "Exponential" = 2)) %>% 
  column_spec(3, color = "black",
              background = spec_color(tmp_lm$RMSE, begin = .25, end = 1, direction = -1,
                                      option = "A")) %>% 
  column_spec(5, color = "black",
              background = spec_color(tmp_quad$RMSE, begin = .25, end = 1, direction = -1,
                                      option = "A")) %>% 
  column_spec(7, color = "black",
              background = spec_color(tmp_cube$RMSE, begin = .25, end = 1, direction = -1,
                                      option = "A")) %>% 
  column_spec(9, color = "black",
              background = spec_color(tmp_exp$RMSE, begin = .25, end = 1, direction = -1,
                                      option = "A")) 

```


The following figure depicts model performance, in terms of RMSE, across various 
change-points for each of the methods evaluated:
```{r, echo = FALSE,out.width="100%"}
SSD_res_standard$ssd_fits %>% 
  ggplot(aes(cp,rmse, color = periodicity)) +
  geom_line() +
  facet_wrap(~model) +
  theme_bw()

```


### Linear Models

The following figure depicts the optimal linear model along with the 4 other nearest
change-points on either side of the optimal change-point
```{r, echo = FALSE, warning = FALSE, out.width="100%"}
tmp <- SSD_res_standard$ssd_fits %>% 
  group_by(model, periodicity) %>% 
  filter(rmse == min(rmse)) %>% 
  select(model,cp,periodicity) %>% 
  mutate(cp_range = map(cp,~(-4*7+.):(4*7+.))) %>% 
  unnest(cp_range) %>% 
  select(model,cp=cp_range,periodicity) %>% 
  inner_join(SSD_res_standard$ssd_fits,by = join_by(model, cp,periodicity)) %>% 
  select(model,cp,periodicity,rmse,pred) %>% 
  unnest() %>% 
  ungroup()


tmp %>% 
  filter(periodicity) %>% 
  filter(model == "lm") %>% 
  mutate(label = paste0(cp," days/",cp/7," wks; RMSE = ",round(rmse,3))) %>% 
  ggplot(aes(period,n)) +
  geom_point() + 
  geom_line(aes(y=pred1), color = "red") +
  geom_vline(aes(xintercept = cp), linetype = 2) +
  scale_x_reverse() +
  facet_wrap(~label) +
  theme_bw() +
  ggtitle("Linear Models w/ Periodicity Near Optimal CP")
```
```{r, echo = FALSE, warning = FALSE, out.width="100%"}
tmp %>% 
  filter(!periodicity) %>% 
  filter(model == "lm") %>% 
  mutate(label = paste0(cp," days/",cp/7," wks; RMSE = ",round(rmse,3))) %>% 
  ggplot(aes(period,n)) +
  geom_point() + 
  geom_line(aes(y=pred1), color = "red")+
  geom_vline(aes(xintercept = cp), linetype = 2) +
  scale_x_reverse() +
  facet_wrap(~label) +
  theme_bw() +
  ggtitle("Linear Models w/o Periodicity Near Optimal CP")
```


### Quadratic Models

The following figure depicts the optimal quadratic model along with the 4 other nearest
change-points on either side of the optimal change-point
```{r, echo = FALSE, warning = FALSE, out.width="100%"}

tmp %>% 
  filter(periodicity) %>% 
  filter(model == "quad") %>% 
  mutate(label = paste0(cp," days/",cp/7," wks; RMSE = ",round(rmse,3))) %>% 
  ggplot(aes(period,n)) +
  geom_point() + 
  geom_line(aes(y=pred1), color = "red")+
  geom_vline(aes(xintercept = cp), linetype = 2) +
  scale_x_reverse() +
  facet_wrap(~label) +
  theme_bw() +
  ggtitle("Quadratic Models w/ Periodicity Near Optimal CP")
```

```{r, echo = FALSE, warning = FALSE, out.width="100%"}

tmp %>% 
  filter(!periodicity) %>% 
  filter(model == "quad") %>% 
  mutate(label = paste0(cp," days/",cp/7," wks; RMSE = ",round(rmse,3))) %>% 
  ggplot(aes(period,n)) +
  geom_point() + 
  geom_line(aes(y=pred1), color = "red")+
  geom_vline(aes(xintercept = cp), linetype = 2) +
  scale_x_reverse() +
  facet_wrap(~label) +
  theme_bw() +
  ggtitle("Quadratic Models w/o Periodicity Near Optimal CP")
```

### Cubic Models

The following figure depicts the optimal cubic model along with the 4 other nearest
change-points on either side of the optimal change-point
```{r, echo = FALSE, warning = FALSE, out.width="100%"}

tmp %>% 
  filter(periodicity) %>% 
  filter(model == "quad") %>% 
  mutate(label = paste0(cp," days/",cp/7," wks; RMSE = ",round(rmse,3))) %>% 
  ggplot(aes(period,n)) +
  geom_point() + 
  geom_line(aes(y=pred1), color = "red")+
  scale_x_reverse() +
  facet_wrap(~label) +
  theme_bw() +
  ggtitle("Cubic Models w/ Periodicity Near Optimal CP")
```

```{r, echo = FALSE, warning = FALSE, out.width="100%"}

tmp %>% 
  filter(!periodicity) %>% 
  filter(model == "quad") %>% 
  mutate(label = paste0(cp," days/",cp/7," wks; RMSE = ",round(rmse,3))) %>% 
  ggplot(aes(period,n)) +
  geom_point() + 
  geom_line(aes(y=pred1), color = "red")+
  scale_x_reverse() +
  facet_wrap(~label) +
  theme_bw() +
  ggtitle("Cubic Models w/o Periodicity Near Optimal CP")
```

### Exponential Models

The following figure depicts the optimal exponential model along with the 4 other nearest
change-points on either side of the optimal change-point
```{r, echo = FALSE, warning = FALSE, out.width="100%"}

tmp %>% 
  filter(periodicity) %>% 
  filter(model == "exp") %>% 
  mutate(label = paste0(cp," days/",cp/7," wks; RMSE = ",round(rmse,3))) %>% 
  ggplot(aes(period,n)) +
  geom_point() + 
  geom_line(aes(y=pred1), color = "red")+
  scale_x_reverse() +
  facet_wrap(~label) +
  theme_bw() +
  ggtitle("Exponential Models w/ Periodicity Near Optimal CP")
```

```{r, echo = FALSE, warning = FALSE, out.width="100%"}

tmp %>% 
  filter(!periodicity) %>% 
  filter(model == "exp") %>% 
  mutate(label = paste0(cp," days/",cp/7," wks; RMSE = ",round(rmse,3))) %>% 
  ggplot(aes(period,n)) +
  geom_point() + 
  geom_line(aes(y=pred1), color = "red")+
  scale_x_reverse() +
  facet_wrap(~label) +
  theme_bw() +
  ggtitle("Exponential Models w/o Periodicity Near Optimal CP")
```




# Bootstrapping CP Approach

This section summarizes results using counts of SSD-related visits.

The following figure depicts the in-sample and out-of-sample performance
(MSE) of various bounds on the opportunity window and different trends.

```{r, echo = FALSE}
inner_join(in_sample_mse_ssd,out_of_sample_mse_ssd,by = join_by(cp, model)) %>%
  inner_join(select(kfold_mse_ssd,model,cp,out_mse_other_boot=mean_mse),by = join_by(cp, model)) %>% 
  gather(key = key, value = value, -model, -cp)  %>% 
  mutate(label = ifelse(key == "in_mse", "In-Sample",
                        ifelse(key=="out_mse","Out-of-Sample (Aggregate)","Out-of-Sample (K-fold)"))) %>% 
  inner_join(tibble(model=c("linear","quad","cube"),
                    model_lab = c("Linear", "Quadratic", "Cubic")),
             by = join_by(model)) %>% 
  ggplot(aes(cp,value,color = model_lab)) +
  geom_line() +
  facet_wrap(~label,scale = "free_y") +
  theme_bw() +
  ylab("MSE") +
  xlab("Opportunity Window Upper Bound") +
  theme(legend.title = element_blank(),
        legend.position = "bottom")
```

The following table depicts the top 10 specifications based on either aggregate or
k-fold out-of-sample performance:

```{r, echo = FALSE}
tab1 <- out_of_sample_mse_ssd %>% 
  ungroup() %>% 
  arrange(out_mse) %>% 
  mutate(cp = -cp) %>% 
  inner_join(tibble(model=c("linear","quad","cube"),
                    model_lab = c("Linear", "Quadratic", "Cubic")),
             by = join_by(model)) %>% 
  select(cp,model_lab,out_mse) %>% 
  mutate(Weeks = cp/7) %>% 
  rename(`Days`=cp,Model=model_lab,MSE=out_mse) %>% 
  select(Weeks, Days, Model, MSE) %>% 
  slice(1:10) %>% 
  mutate(rank = row_number()) %>% 
  mutate(MSE = round(MSE,2)) %>% 
  select(rank,everything())

tab2 <- kfold_mse_ssd %>% 
  select(model,cp,out_mse=mean_mse) %>% 
  arrange(out_mse) %>% 
  mutate(cp = -cp) %>% 
  inner_join(tibble(model=c("linear","quad","cube"),
                    model_lab = c("Linear", "Quadratic", "Cubic")),
             by = join_by(model)) %>% 
  select(cp,model_lab,out_mse) %>% 
  mutate(out_mse = round(out_mse,2)) %>% 
  mutate(Weeks = cp/7) %>% 
  rename(`Days`=cp,Model=model_lab,MSE=out_mse) %>% 
  select(Weeks, Days, Model, MSE) %>% 
  slice(1:10)

cbind(tab1,tab2) %>% 
  kable(align = 'c', booktabs = TRUE) %>% 
  kable_styling(full_width = F) %>% 
  add_header_above(c(" " = 1, "Aggregate Out-of-Sample" = 4, "K-Fold Out-of-Sample" = 4))
```


The following figure depicts the observed and expected trend for the top
9 models based on **99-fold out-of-sample** performance:

```{r, echo = FALSE, message=FALSE,warning=FALSE,out.width="100%"}
kfold_mse_ssd %>% 
  arrange(mean_mse) %>% 
  slice(1:9) %>% 
  inner_join(tibble(model=c("linear","quad","cube"),
                    model_lab = c("Linear", "Quadratic", "Cubic")),
             by = join_by(model)) %>% 
  mutate(label = paste0(model_lab,": ",-cp, " days/",(-cp/7),"wks \n RMSE ",round(mean_mse,2))) %>% 
  inner_join(cp_fits_ssd,by = join_by(cp, model)) %>% 
  ggplot(aes(-days_since_index,n)) +
  geom_point(size = 0.8) +
  geom_line(aes(y=combined), color = "blue", size = 0.7) +
  geom_line(aes(y=expected), color = "red", size = 0.7) +
  geom_vline(aes(xintercept = -cp), linetype = 2) +
  facet_wrap(~label) +
  scale_x_reverse() +
  theme_bw() +
  ylab("Number of Patients") +
  xlab("Days Before Diagnosis") 

```


### Summary of Model Performance Across Change-points

The following table summarizes the out-of-sample and 99-fold performance (RMSE) 
along with the implied number of missed opportunities for each method across the 
different change-points evaluated

```{r, echo = FALSE, message=FALSE}
tmp1 <- out_of_sample_mse_ssd %>% 
  select(model,cp,out_mse) %>% 
  mutate(out_mse = round(out_mse,2)) %>% 
  spread(key = model, value = out_mse) %>% 
  arrange(desc(cp)) %>% 
  ungroup()

tmp2 <- kfold_mse_ssd %>% 
  select(model,cp,mean_mse) %>% 
  mutate(mean_mse = round(mean_mse,2)) %>% 
  spread(key = model, value = mean_mse) %>% 
  arrange(desc(cp)) 

tmp3 <- cp_fits_ssd %>% 
  group_by(model,cp) %>% 
  filter(days_since_index>=cp) %>% 
  summarise(n_miss = sum(n-expected)) %>% 
  ungroup() %>% 
  mutate(n_miss = round(n_miss,0)) %>% 
  spread(key = model, value = n_miss) %>% 
  arrange(desc(cp))


tmp_lm <- inner_join(select(tmp1,cp,`Out-of-sample` = linear),
                     select(tmp2,cp,`K-fold` = linear)) %>% 
  inner_join(select(tmp3,cp,`N Miss Visits` = linear)) %>%
  mutate(weeks = -cp/7) %>% 
  mutate(cp = -cp) %>% 
  select(weeks,days=cp,`Out-of-sample RMSE`=`Out-of-sample`,`K-fold RMSE`=`K-fold`,`N Miss Visits`) 

tmp_quad <- inner_join(select(tmp1,cp,`Out-of-sample` = quad),
                       select(tmp2,cp,`K-fold` = quad)) %>% 
  inner_join(select(tmp3,cp,`N Miss Visits` = quad)) %>%
  mutate(weeks = -cp/7) %>% 
  mutate(cp = -cp) %>% 
  select(`Out-of-sample RMSE`=`Out-of-sample`,`K-fold RMSE`=`K-fold`,`N Miss Visits`) 

tmp_cube <- inner_join(select(tmp1,cp,`Out-of-sample` = cube),
                       select(tmp2,cp,`K-fold` = cube)) %>% 
  inner_join(select(tmp3,cp,`N Miss Visits` = cube)) %>%
  mutate(weeks = -cp/7) %>% 
  mutate(cp = -cp) %>% 
  select(`Out-of-sample RMSE`=`Out-of-sample`,`K-fold RMSE`=`K-fold`,`N Miss Visits`) 

tmp <- cbind(tmp_lm,tmp_quad,tmp_cube) 

j11 <- which.min(tmp[,3])
tmp[j11,3] <- tmp[j11,3] %>% cell_spec(bold = TRUE)

j12 <- which.min(tmp[,4])
tmp[j12,4] <- tmp[j12,4] %>% cell_spec(bold = TRUE)

j21 <- which.min(tmp[,6])
tmp[j21,6] <- tmp[j21,6] %>% cell_spec(bold = TRUE)

j22 <- which.min(tmp[,7])
tmp[j22,7] <- tmp[j22,7] %>% cell_spec(bold = TRUE)


j31 <- which.min(tmp[,9])
tmp[j31,9] <- tmp[j31,9] %>% cell_spec(bold = TRUE)

j32 <- which.min(tmp[,10])
tmp[j32,10] <- tmp[j32,10] %>% cell_spec(bold = TRUE)

tmp %>% 
  kable(align = 'c', booktabs = TRUE,escape = FALSE) %>% 
  kable_styling(full_width = F) %>% 
  add_header_above(c("Change Point" = 2, "Linear" = 3, "Quadratic" = 3, "Cubic" = 3)) %>% 
  column_spec(3, color = "black",
              background = spec_color(tmp_lm[["Out-of-sample RMSE"]], begin = .25, end = 1, direction = -1,
                                      option = "A")) %>% 
  column_spec(6, color = "black",
              background = spec_color(tmp_quad[["Out-of-sample RMSE"]], begin = .25, end = 1, direction = -1,
                                      option = "A")) %>% 
  column_spec(9, color = "black",
              background = spec_color(tmp_cube[["Out-of-sample RMSE"]], begin = .25, end = 1, direction = -1,
                                      option = "A")) %>% 
  column_spec(4, color = "black",
              background = spec_color(tmp_lm[["K-fold RMSE"]], begin = .25, end = 1, direction = -1,
                                      option = "A")) %>% 
  column_spec(7, color = "black",
              background = spec_color(tmp_quad[["K-fold RMSE"]], begin = .25, end = 1, direction = -1,
                                      option = "A")) %>% 
  column_spec(10, color = "black",
              background = spec_color(tmp_cube[["K-fold RMSE"]], begin = .25, end = 1, direction = -1,
                                      option = "A"))
```



### Linear Models

The following figure depicts the optimal linear model (based on 99-fold performance) 
along with the 4 other nearest change-points on either side of the optimal change-point
```{r, echo = FALSE, message=FALSE, warning = FALSE, out.width="100%"}

tmp <- kfold_mse_ssd %>% 
  group_by(model) %>% 
  filter(mean_mse == min(mean_mse)) %>% 
  select(model,cp,rmse=mean_mse) %>% 
  mutate(cp_range = map(cp,~(-4*7+.):(4*7+.))) %>% 
  unnest(cp_range) %>% 
  select(model,cp = cp_range) %>% 
  inner_join(kfold_mse_ssd) %>% 
  select(model,cp,rmse = mean_mse) %>% 
  ungroup() %>% 
  inner_join(cp_fits_ssd)


tmp %>% 
  filter(model == "linear") %>% 
  mutate(label = paste0(-cp," days/",-cp/7," wks; RMSE = ",round(rmse,2))) %>% 
  mutate(period = -days_since_index) %>% 
  ggplot(aes(period,n)) +
  geom_point() + 
  geom_line(aes(y=combined), color = "blue") +
  geom_line(aes(y=expected), color = "red") +
  geom_vline(aes(xintercept = -cp), linetype = 2) +
  scale_x_reverse() +
  facet_wrap(~label) +
  theme_bw() +
  ggtitle("Linear Models w/ Periodicity Near Optimal CP")
```

### Quadratic Models

The following figure depicts the optimal quadratic model (based on 99-fold performance) 
along with the 4 other nearest change-points on either side of the optimal change-point
```{r, echo = FALSE, message=FALSE, warning = FALSE, out.width="100%"}

tmp %>% 
  filter(model == "quad") %>% 
  mutate(label = paste0(-cp," days/",-cp/7," wks; RMSE = ",round(rmse,2))) %>% 
  mutate(period = -days_since_index) %>% 
  ggplot(aes(period,n)) +
  geom_point() + 
  geom_line(aes(y=combined), color = "blue") +
  geom_line(aes(y=expected), color = "red") +
  geom_vline(aes(xintercept = -cp), linetype = 2) +
  scale_x_reverse() +
  facet_wrap(~label) +
  theme_bw() +
  ggtitle("Linear Models w/ Periodicity Near Optimal CP")
```

### Cubic Models

The following figure depicts the optimal cubic model (based on 99-fold performance) 
along with the 4 other nearest change-points on either side of the optimal change-point
```{r, echo = FALSE, message=FALSE, warning = FALSE, out.width="100%"}

tmp %>% 
  filter(model == "cube") %>% 
  mutate(label = paste0(-cp," days/",-cp/7," wks; RMSE = ",round(rmse,2))) %>% 
  mutate(period = -days_since_index) %>% 
  ggplot(aes(period,n)) +
  geom_point() + 
  geom_line(aes(y=combined), color = "blue") +
  geom_line(aes(y=expected), color = "red") +
  geom_vline(aes(xintercept = -cp), linetype = 2) +
  scale_x_reverse() +
  facet_wrap(~label) +
  theme_bw() +
  ggtitle("Linear Models w/ Periodicity Near Optimal CP")
```