---
title: "Risk Factor Report"
date: '`r strftime(Sys.time(), format = "%B %d, %Y")`'
output: html_document
params:
  cond:
    value: x
---

```{r setup, include=FALSE}
knitr::opts_chunk$set(
      echo    = FALSE
    , warning = FALSE
    , message = FALSE
)

library(tidyverse)
library(kableExtra)
library(ggplot2)
library(lubridate)

# params <- list()
# params$cond <- "dengue"

# load delay_parms
load("/Shared/AML/params/final_delay_params.RData")

delay_params <- final_delay_params[[proj_name]]

risk_model_base_path <- paste0(delay_params$out_path,"risk_models/")

# load results data
# load("/Volumes/AML/small_dbs/tb/truven/enroll_restrict_365/delay_results/risk_models/ssd_miss_risk_models.RData")
load(paste0(risk_model_base_path,"ssd_miss_risk_models.RData"))

# setup better labels
better_labels <- tribble(~term,~label,
                         '(Intercept)', '(Intercept)'  ,
                         'age_cat(17,34]', 'Age 18-34'  ,
                         'age_cat(34,44]', 'Age 35-44'  ,
                         'age_cat(44,54]', 'Age 45-54'  ,
                         'age_cat(54,64]', 'Age 55-64'  ,
                         'age_cat(64,130]', 'Age >= 65'  ,
                         'femaleTRUE', 'Female'  ,
                         'obs_stayTRUE', 'Observational Stay'  ,
                         'rural', 'Rural'  ,
                         'setting_labelAll three', 'Outpatient, ED, and Inpatient'  ,
                         'setting_labelED and inpatient', 'ED and Inpatient'  ,
                         'setting_labelED only', 'ED Only'  ,
                         'setting_labelInpatient only', 'Inpatient Only'  ,
                         'setting_labelOut and ED', 'Outpatient and ED'  ,
                         'setting_labelOut and inpatient', 'Outpatient and Inpatient'  ,
                         'setting_labelnone', 'Not Outpatient, ED or Inpatient'  ,
                         "inpatient", "Inpatient",
                         'sourcemdcr', 'Medicare'  ,
                         'sourcemedicaid', 'Medicaid',
                         "weekendTRUE", "Weekend Visit",
                         'raceBlack', 'Black race',
                         'raceHispanic', 'Hispanic race',
                         'raceMissing/Unknown', 'Missing/Unknown race',
                         'raceOther', 'Other race',
                         'asthma_prior_cp', 'Asthma dx prior to change point',
                         'copd_prior_cp', 'COPD dx prior to change point',
                         'IPD_prior_cp', 'IPD dx prior to change point',
                          'ID_consult', 'ID consult during visit',
                         'chest_ct_prior_cp', 'Chest CT dx prior to change point',
                         'chest_xray_prior_cp', 'Chest x-ray dx prior to change point',
                         'top2_high_inc_state_baddley', 'Residing in state with incidence >= 1.38',
                         'top2_high_inc_state_baddley:ID_consult', 'Residing in state with incidence >= 1.38 * ID consult during visit',
                         'top5_truven_inc_states', 'Residing in top 5 highest truven inc state',
                         'resp_antibiotic_drugs_window', 'Respiratory abx rx during delay window',
                         'inhalers_window', 'Inhaler rx during delay window')

better_labels <- better_labels %>% 
  bind_rows(ssd_miss_risk_models$miss_opp_res %>% 
              select(term) %>% 
              filter(grepl("setting_label", term)) %>% 
              mutate(label = stringr::str_remove_all(term, "setting_label")))
```


# Delay Risk Factor Report for `r params$cond`

### Note: The year 2001 was excluded from the analyses below as no index visits occured during that year. This has to do with the 365 day enrollment requirement.

```{r, echo = FALSE}
index_locations %>% count(year) %>%
  left_join(tibble(year = 2001:2022), .) %>% 
  mutate(year = as.character(year), 
         n = replace_na(n, 0)) %>% 
  ggplot(aes(x = year, y = n)) +
  geom_point() + 
  ylab("Number of index cases") +
  xlab("Year") +
  theme_bw() + 
  theme(axis.text.x = element_text(angle = 90, vjust = 0.5, hjust=1))
```

### Missed Opportunities

The following tables depicts results for the risk model for experiencing a missed 
opportunity at a given visit. All missed visits and index dates are included in 
this model with an outcome of 1 assigned to missed opportunities and 0 to index 
diagnoses.

Note: All models below were adjusted for year and month of visit

*The following risk model pertains to all observations*

```{r, echo = FALSE}

ssd_miss_risk_models$miss_opp_res %>% 
  mutate(`Odds Ratio` = paste0(formatC(est, digits = 3, format = "g", flag= "#"),
                               " (",
                               formatC(low, digits = 3, format = "g", flag= "#"),
                               "-",
                               formatC(high, digits = 3, format = "g", flag= "#"),")")) %>% 
  inner_join(better_labels) %>% 
  filter(!str_detect(term, 'year')) %>% 
  filter(!str_detect(term, 'month')) %>% 
  select(label, `Odds Ratio`) %>% 
  kableExtra::kable() %>% 
  kableExtra::kable_styling(full_width = F)
```

*The following risk model pertains to all observations with an any inpatient indicator instead*

```{r, echo = FALSE}

ssd_miss_risk_models$miss_opp_res_inpatient_ind %>% 
  mutate(`Odds Ratio` = paste0(formatC(est, digits = 3, format = "g", flag= "#"),
                               " (",
                               formatC(low, digits = 3, format = "g", flag= "#"),
                               "-",
                               formatC(high, digits = 3, format = "g", flag= "#"),")")) %>% 
  inner_join(better_labels) %>% 
  filter(!str_detect(term, 'year')) %>% 
  filter(!str_detect(term, 'month')) %>% 
  select(label, `Odds Ratio`) %>% 
  kableExtra::kable() %>% 
  kableExtra::kable_styling(full_width = F)
```

### Missed Patients

The following table presents results for the risk model estimating the likelihood
a given patient would experience a missed opportunity. Each patient is assigned 
an outcome of 1 if they were missed (in a particular simulation) and 0 if they 
were not missed.

Note: All models were adjusted for year and month of the index visit.

*The following risk model pertains to all observations*

```{r, echo = FALSE}

ssd_miss_risk_models$miss_delay_pat_res %>% 
  mutate(`Odds Ratio` = paste0(formatC(est, digits = 3, format = "g", flag= "#"),
                               " (",
                               formatC(low, digits = 3, format = "g", flag= "#"),
                               "-",
                               formatC(high, digits = 3, format = "g", flag= "#"),")")) %>% 
  inner_join(better_labels) %>% 
  filter(!str_detect(term, 'year')) %>% 
  filter(!str_detect(term, 'month')) %>% 
  select(label, `Odds Ratio`) %>% 
  kableExtra::kable() %>% 
  kableExtra::kable_styling(full_width = F)
```



### Delay Duration

The following table presents results for the model estimating the duration 
of delays. In each model patients were assigned an integer value based on days 
between index and their earliest missed opportunity. Patients without a missed opportunity in a given trial were excluded from the analysis.
**This analysis utilizes a linear regression model with duration 
of delay as the outcome.**

Note: All models were adjusted for year and month of the index visit.

*The following risk model pertains to all observations*

```{r, echo = FALSE}

ssd_miss_risk_models$miss_dur_res %>% 
  mutate(`Estimate (Days)` = paste0(formatC(est, digits = 3, format = "g", flag= "#"),
                                    " (",
                                    formatC(low, digits = 3, format = "g", flag= "#"),
                                    "-",
                                    formatC(high, digits = 3, format = "g", flag= "#"),")")) %>% 
  inner_join(better_labels) %>% 
  filter(!str_detect(term, 'year')) %>% 
  filter(!str_detect(term, 'month')) %>%
  select(label, `Estimate (Days)`) %>% 
  kableExtra::kable() %>% 
  kableExtra::kable_styling(full_width = F)
```

The following table presents results for the model estimating the duration 
of delays. In each model patients were assigned an integer value based on days 
between index and their earliest missed opportunity. Patients without a missed opportunity in a given trial were excluded from the analysis.
**This analysis utilizes a Log-normal accelerated failure time model.
Since there is no censoring in our case, this model is simply a linear regression model with 
the log transformed duration of delay as the outcome**. 


**Interpretation of estimate: The estimate from this model is interpreted as a multiplicative effect on the
median duration of delay. E.g. if the estimate for a dichotomous risk factor A is 1.6, we would
interpret this as: the median duration of delay for those exposed to risk factor A is 1.6 times the median duration 
of delay for those not expose to risk factor A (or the median duration of delay is 60% greater among those exposed to risk factor A).**

Note: All models were adjusted for year and month of the index visit.

*The following risk model pertains to all observations*

```{r, echo = FALSE}

ssd_miss_risk_models$miss_dur_res_log_normal %>% 
  mutate(`Estimate` = paste0(formatC(est, digits = 3, format = "g", flag= "#"),
                                    " (",
                                    formatC(low, digits = 3, format = "g", flag= "#"),
                                    "-",
                                    formatC(high, digits = 3, format = "g", flag= "#"),")")) %>% 
  inner_join(better_labels) %>% 
  filter(!str_detect(term, 'year')) %>% 
  filter(!str_detect(term, 'month')) %>%
  select(label, `Estimate`) %>% 
  kableExtra::kable() %>% 
  kableExtra::kable_styling(full_width = F)
```


The following table presents results for the model estimating the duration 
of delays. In each model patients were assigned an integer value based on days 
between index and their earliest missed opportunity. Patients without a missed opportunity in a given trial were excluded from the analysis.
**This analysis utilizes a Weibull accelerated failure time model with no censoring.** 

**Interpretation of estimate: The estimate from this model is interpreted as a multiplicative effect on the 
time to the earliest missed opportunity., which can also be interpreted as the duration of delay. E.g. if the estimate for a dichotomous risk factor A is 1.6, we would
interpret this as: those exposed to risk factor A are estimated to have longer times to the earliest missed opportunity (or longer delays) than those not exposed
by a multiplicative factor of 1.6.**

Note: All models were adjusted for year and month of the index visit.

*The following risk model pertains to all observations*


```{r, echo = FALSE}

ssd_miss_risk_models$miss_dur_res_weibull %>% 
  mutate(`Estimate` = paste0(formatC(est, digits = 3, format = "g", flag= "#"),
                                    " (",
                                    formatC(low, digits = 3, format = "g", flag= "#"),
                                    "-",
                                    formatC(high, digits = 3, format = "g", flag= "#"),")")) %>% 
  inner_join(better_labels) %>% 
  filter(!str_detect(term, 'year')) %>% 
  filter(!str_detect(term, 'month')) %>%
  select(label, `Estimate`) %>% 
  kableExtra::kable() %>% 
  kableExtra::kable_styling(full_width = F)
```

