---
title: "Risk Factor Report"
date: '`r strftime(Sys.time(), format = "%B %d, %Y")`'
output: html_document
params:
  cond:
    value: x
---

```{r setup, include=FALSE}
knitr::opts_chunk$set(
      echo    = FALSE
    , warning = FALSE
    , message = FALSE
)

library(tidyverse)
library(kableExtra)
library(ggplot2)
library(lubridate)

# params <- list()
# params$cond <- "dengue"

# load delay_parms
load("/Shared/AML/params/final_delay_params.RData")

delay_params <- final_delay_params[[proj_name]]

risk_model_base_path <- paste0(delay_params$out_path,"risk_models/")

# load results data
# load("/Volumes/AML/small_dbs/tb/truven/enroll_restrict_365/delay_results/risk_models/ssd_miss_risk_models.RData")
load(paste0(risk_model_base_path,"ssd_miss_risk_models.RData"))

# setup better labels
better_labels <- tribble(~term,~label,
                         '(Intercept)', '(Intercept)'  ,
                         'age_cat(17,34]', 'Age 18-34'  ,
                         'age_cat(34,44]', 'Age 35-44'  ,
                         'age_cat(44,54]', 'Age 45-54'  ,
                         'age_cat(54,64]', 'Age 55-64'  ,
                         'age_cat(64,130]', 'Age >= 65'  ,
                         'femaleTRUE', 'Female'  ,
                         'obs_stayTRUE', 'Observational Stay'  ,
                         'rural', 'Rural'  ,
                         'setting_labelAll three', 'Outpatient, ED, and Inpatient'  ,
                         'setting_labelED and inpatient', 'ED and Inpatient'  ,
                         'setting_labelED only', 'ED Only'  ,
                         'setting_labelInpatient only', 'Inpatient Only'  ,
                         'setting_labelOut and ED', 'Outpatient and ED'  ,
                         'setting_labelOut and inpatient', 'Outpatient and Inpatient'  ,
                         'setting_labelnone', 'Not Outpatient, ED or Inpatient'  ,
                         "inpatient", "Inpatient",
                         'sourcemdcr', 'Medicare'  ,
                         'sourcemedicaid', 'Medicaid',
                         "weekendTRUE", "Weekend Visit",
                         'raceBlack', 'Black race',
                         'raceHispanic', 'Hispanic race',
                         'raceMissing/Unknown', 'Missing/Unknown race',
                         'raceOther', 'Other race',
                         "abx", "Antibiotic rx during visit",
                         "opioid", "Opioid rx during visit",
                         "oral_steroids", "Oral steroid rx during visit",
                         "inhalers", "Inhaler rx during visit",
                         "diuretic", "Diuretic rx during visit",
                         "antibiotic", "Antibiotic rx during visit",
                         "antihistamine", "Antihistamine rx during visit",
                         "antiinflammatory", "Anti-inflammatory rx during visit",
                         "antiacid", "Antiacid rx during visit",
                         "nasal_spray", "Nasal spray rx during visit",
                         "cough_suppressant", "Cough suppressant rx during visit",
                         "ppi", "PPI rx during visit",
                         "antifungal", "Antifungal rx during visit",
                         "abx_window", "Antibiotic rx during delay window",
                         "opioid_window", "Opioid rx during delay window",
                         "oral_steroids_window", "Oral steroid rx during delay window",
                         "inhalers_window", "Inhaler rx during delay window",
                         "diuretic_drugs_window", "Diuretic rx during delay window",
                         "antibiotic_drugs_window", "Antibiotic rx during delay window",
                         "antihistamine_drugs_window", "Antihistamine rx during delay window",
                         "antiinflammatory_drugs_window", "Anti-inflammatory rx during delay window",
                         "antiacid_drugs_window", "Antiacid rx during delay window",
                         "nasal_spray_drugs_window", "Nasal spray rx during delay window",
                         "cough_suppressant_drugs_window", "Cough suppressant rx during delay window",
                         "ppi_drugs_window", "PPI rx during delay window",
                         "antifungal_drugs_window", "Antifungal rx during delay window",
                         "ID_consult", "ID consult during visit",
                         "any_obesity", "Any obesity dx prior to index",
                          "morbid_obesity", "Morbid obesity dx prior to index")

better_labels <- better_labels %>% 
  bind_rows(ssd_miss_risk_models$miss_opp_res %>% 
              select(term) %>% 
              filter(grepl("setting_label", term)) %>% 
              mutate(label = stringr::str_remove_all(term, "setting_label")))
```


# Delay Risk Factor Report for `r params$cond`

### Note: The year 2001 and 2002 were excluded from the analyses below as no index cases occured in those years. This has to do with the 730 day enrollment requirement.

```{r, echo = FALSE}
index_locations %>% count(year) %>%
  left_join(tibble(year = 2001:2022), .) %>% 
  mutate(year = as.character(year), 
         n = replace_na(n, 0)) %>% 
  ggplot(aes(x = year, y = n)) +
  geom_point() + 
  ylab("Number of index cases") +
  xlab("Year") +
  theme_bw() + 
  theme(axis.text.x = element_text(angle = 90, vjust = 0.5, hjust=1))
```

### Missed Opportunities

The following tables depicts results for the risk model for experiencing a missed 
opportunity at a given visit. All missed visits and index dates are included in 
this model with an outcome of 1 assigned to missed opportunities and 0 to index 
diagnoses.

Note: All models below were adjusted for year and month of visit

*The following risk model pertains to all observations (CCAE, MDCR and Medicaid)*

```{r, echo = FALSE}

ssd_miss_risk_models$miss_opp_res %>% 
  mutate(`Odds Ratio` = paste0(formatC(est, digits = 3, format = "g", flag= "#"),
                               " (",
                               formatC(low, digits = 3, format = "g", flag= "#"),
                               "-",
                               formatC(high, digits = 3, format = "g", flag= "#"),")")) %>% 
  inner_join(better_labels) %>% 
  filter(!str_detect(term, 'year')) %>% 
  filter(!str_detect(term, 'month')) %>% 
  select(label, `Odds Ratio`) %>% 
  kableExtra::kable() %>% 
  kableExtra::kable_styling(full_width = F)
```

*The following risk model pertains to all observations (CCAE, MDCR and Medicaid) with an any inpatient indicator instead*

```{r, echo = FALSE}

ssd_miss_risk_models$miss_opp_res_inpatient_ind %>% 
  mutate(`Odds Ratio` = paste0(formatC(est, digits = 3, format = "g", flag= "#"),
                               " (",
                               formatC(low, digits = 3, format = "g", flag= "#"),
                               "-",
                               formatC(high, digits = 3, format = "g", flag= "#"),")")) %>% 
  inner_join(better_labels) %>% 
  filter(!str_detect(term, 'year')) %>% 
  filter(!str_detect(term, 'month')) %>% 
  select(label, `Odds Ratio`) %>% 
  kableExtra::kable() %>% 
  kableExtra::kable_styling(full_width = F)
```


*The following risk model pertains to Medicaid patients*

```{r, echo = FALSE}

ssd_miss_risk_models$miss_opp_res_med %>% 
  mutate(`Odds Ratio` = paste0(formatC(est, digits = 3, format = "g", flag= "#"),
                               " (",
                               formatC(low, digits = 3, format = "g", flag= "#"),
                               "-",
                               formatC(high, digits = 3, format = "g", flag= "#"),")")) %>%   
  inner_join(better_labels) %>% 
  filter(!str_detect(term, 'year')) %>% 
  filter(!str_detect(term, 'month')) %>% 
  select(label, `Odds Ratio`) %>% 
  kableExtra::kable() %>% 
  kableExtra::kable_styling(full_width = F)
```

*The following risk model pertains to Medicaid patients with an any inpatient indicator instead*

```{r, echo = FALSE}

ssd_miss_risk_models$miss_opp_res_med_inpatient_ind %>% 
  mutate(`Odds Ratio` = paste0(formatC(est, digits = 3, format = "g", flag= "#"),
                               " (",
                               formatC(low, digits = 3, format = "g", flag= "#"),
                               "-",
                               formatC(high, digits = 3, format = "g", flag= "#"),")")) %>% 
  inner_join(better_labels) %>% 
  filter(!str_detect(term, 'year')) %>% 
  filter(!str_detect(term, 'month')) %>% 
  select(label, `Odds Ratio`) %>% 
  kableExtra::kable() %>% 
  kableExtra::kable_styling(full_width = F)
```

### Missed Patients

The following tables depict results for the risk models estimating the likelihood
a given patient would experience a missed opportunity. Each patient is assigned 
an outcome of 1 if they were missed (in a particular simulation) and 0 if they 
were not missed.

Note: All models were adjusted for year and month of the index visit.

*The following risk model pertains to all observations (CCAE, MDCR and Medicaid)*

```{r, echo = FALSE}

ssd_miss_risk_models$miss_delay_pat_res %>% 
  mutate(`Odds Ratio` = paste0(formatC(est, digits = 3, format = "g", flag= "#"),
                               " (",
                               formatC(low, digits = 3, format = "g", flag= "#"),
                               "-",
                               formatC(high, digits = 3, format = "g", flag= "#"),")")) %>% 
  inner_join(better_labels) %>% 
  filter(!str_detect(term, 'year')) %>% 
  filter(!str_detect(term, 'month')) %>% 
  select(label, `Odds Ratio`) %>% 
  kableExtra::kable() %>% 
  kableExtra::kable_styling(full_width = F)
```

*The following risk model pertains to Medicaid patients*

```{r, echo = FALSE}

ssd_miss_risk_models$miss_delay_pat_res_med %>% 
  mutate(`Odds Ratio` = paste0(formatC(est, digits = 3, format = "g", flag= "#"),
                               " (",
                               formatC(low, digits = 3, format = "g", flag= "#"),
                               "-",
                               formatC(high, digits = 3, format = "g", flag= "#"),")")) %>% 
  inner_join(better_labels) %>% 
  filter(!str_detect(term, 'year')) %>% 
  filter(!str_detect(term, 'month')) %>%
  select(label, `Odds Ratio`) %>% 
  kableExtra::kable() %>% 
  kableExtra::kable_styling(full_width = F)
```


### Delay Duration

The following tables depict results for the  models estimating the duration 
of delays. In each model patients were assigned an integer value based on days 
between index and their earliest missed opportunity. If no delay occured the 
duration was 0 days. For these results a linear model was used to estimate the 
days of duration

Note: All models were adjusted for year and month of the index visit.

*The following risk model pertains to all observations (CCAE, MDCR and Medicaid)*

```{r, echo = FALSE}

ssd_miss_risk_models$miss_dur_res %>% 
  mutate(`Estimate (Days)` = paste0(formatC(est, digits = 3, format = "g", flag= "#"),
                                    " (",
                                    formatC(low, digits = 3, format = "g", flag= "#"),
                                    "-",
                                    formatC(high, digits = 3, format = "g", flag= "#"),")")) %>% 
  inner_join(better_labels) %>% 
  filter(!str_detect(term, 'year')) %>% 
  filter(!str_detect(term, 'month')) %>%
  select(label, `Estimate (Days)`) %>% 
  kableExtra::kable() %>% 
  kableExtra::kable_styling(full_width = F)
```

*The following risk model pertains to Medicaid patients*

```{r, echo = FALSE}

ssd_miss_risk_models$miss_dur_res_med %>% 
  mutate(`Estimate (Days)` = paste0(formatC(est, digits = 3, format = "g", flag= "#"),
                                    " (",
                                    formatC(low, digits = 3, format = "g", flag= "#"),
                                    "-",
                                    formatC(high, digits = 3, format = "g", flag= "#"),")")) %>%   
  inner_join(better_labels) %>% 
  filter(!str_detect(term, 'year')) %>% 
  filter(!str_detect(term, 'month')) %>%
  select(label, `Estimate (Days)`) %>% 
  kableExtra::kable() %>% 
  kableExtra::kable_styling(full_width = F)
```
