---
title: "Risk Factor Report"
date: '`r strftime(Sys.time(), format = "%B %d, %Y")`'
output: html_document
params:
  cond:
    value: x
---

```{r setup, include=FALSE}
knitr::opts_chunk$set(
      echo    = FALSE
    , warning = FALSE
    , message = FALSE
)

library(tidyverse)
library(kableExtra)
library(ggplot2)
library(lubridate)

# params <- list()
# params$cond <- "dengue"

# load delay_parms
load("/Shared/AML/params/final_delay_params.RData")

delay_params <- final_delay_params[[proj_name]]

risk_model_base_path <- paste0(delay_params$out_path,"risk_models/")

# load results data
# load("/Volumes/AML/small_dbs/tb/truven/enroll_restrict_365/delay_results/risk_models/ssd_miss_risk_models.RData")
load(paste0(risk_model_base_path,"ssd_miss_risk_models.RData"))

# setup better labels
better_labels <- tribble(~term,~label,
                         '(Intercept)', '(Intercept)'  ,
                         'age_cat(17,34]', 'Age 18-34'  ,
                         'age_cat(34,44]', 'Age 35-44'  ,
                         'age_cat(44,54]', 'Age 45-54'  ,
                         'age_cat(54,64]', 'Age 55-64'  ,
                         'age_cat(64,130]', 'Age >= 65'  ,
                         'femaleTRUE', 'Female'  ,
                         'obs_stayTRUE', 'Observational Stay'  ,
                         'rural', 'Rural'  ,
                         'setting_labelAll three', 'Outpatient, ED, and Inpatient'  ,
                         'setting_labelED and inpatient', 'ED and Inpatient'  ,
                         'setting_labelED only', 'ED Only'  ,
                         'setting_labelInpatient only', 'Inpatient Only'  ,
                         'setting_labelOut and ED', 'Outpatient and ED'  ,
                         'setting_labelOut and inpatient', 'Outpatient and Inpatient'  ,
                         'setting_labelnone', 'Not Outpatient, ED or Inpatient'  ,
                         'sourcemdcr', 'Medicare'  ,
                         'sourcemedicaid', 'Medicaid',
                         "weekendTRUE", "Weekend Visit",
                         'raceBlack', 'Black race',
                         'raceHispanic', 'Hispanic race',
                         'raceMissing/Unknown', 'Missing/Unknown race',
                         'raceOther', 'Other race',
                         "abx", "Antibiotics during visit",
                         "opioid", "Opioid during visit",
                         "abx_window", "Antibiotics during delay window",
                         "opioid_window", "Opioid during delay window",
                         "ID_consult", "ID consult during visit")

better_labels <- better_labels %>% 
  bind_rows(ssd_miss_risk_models$miss_opp_res %>% 
              select(term) %>% 
              filter(grepl("setting_label", term)) %>% 
              mutate(label = stringr::str_remove_all(term, "setting_label")))
```


# Delay Risk Factor Report for `r params$cond`

### Missed Opportunities

The following tables depicts results for the risk model for experiencing a missed 
opportunity at a given visit. All missed visits and index dates are included in 
this model with an outcome of 1 assigned to missed opportunities and 0 to index 
diagnoses.

The following risk model pertains to all observations (CCAE, MDCR and Medicaid)

```{r, echo = FALSE}

ssd_miss_risk_models$miss_opp_res %>% 
  mutate(`Odds Ratio` = paste0(formatC(est, digits = 3, format = "g", flag= "#"),
                               " (",
                               formatC(low, digits = 3, format = "g", flag= "#"),
                               "-",
                               formatC(high, digits = 3, format = "g", flag= "#"),")")) %>% 
  inner_join(better_labels) %>% 
  select(label, `Odds Ratio`) %>% 
  kableExtra::kable() %>% 
  kableExtra::kable_styling(full_width = F)
```
The following risk model pertains to Medicaid patients

```{r, echo = FALSE}

ssd_miss_risk_models$miss_opp_res_med %>% 
  mutate(`Odds Ratio` = paste0(formatC(est, digits = 3, format = "g", flag= "#"),
                               " (",
                               formatC(low, digits = 3, format = "g", flag= "#"),
                               "-",
                               formatC(high, digits = 3, format = "g", flag= "#"),")")) %>%   inner_join(better_labels) %>% 
  select(label, `Odds Ratio`) %>% 
  kableExtra::kable() %>% 
  kableExtra::kable_styling(full_width = F)
```

### Missed Patients

The following tables depict results for the risk models estimating the likelihood
a given patient would experience a missed opportunity. Each patient is assigned 
an outcome of 1 if they were missed (in a particular simulation) and 0 if they 
were not missed.

The following risk model pertains to all observations (CCAE, MDCR and Medicaid)

```{r, echo = FALSE}

ssd_miss_risk_models$miss_delay_pat_res %>% 
  mutate(`Odds Ratio` = paste0(formatC(est, digits = 3, format = "g", flag= "#"),
                               " (",
                               formatC(low, digits = 3, format = "g", flag= "#"),
                               "-",
                               formatC(high, digits = 3, format = "g", flag= "#"),")")) %>%   inner_join(better_labels) %>% 
  select(label, `Odds Ratio`) %>% 
  kableExtra::kable() %>% 
  kableExtra::kable_styling(full_width = F)
```

The following risk model pertains to Medicaid patients

```{r, echo = FALSE}

ssd_miss_risk_models$miss_delay_pat_res_med %>% 
  mutate(`Odds Ratio` = paste0(formatC(est, digits = 3, format = "g", flag= "#"),
                               " (",
                               formatC(low, digits = 3, format = "g", flag= "#"),
                               "-",
                               formatC(high, digits = 3, format = "g", flag= "#"),")")) %>%   inner_join(better_labels) %>% 
  select(label, `Odds Ratio`) %>% 
  kableExtra::kable() %>% 
  kableExtra::kable_styling(full_width = F)
```


### Delay Duration

The following tables depict results for the  models estimating the duration 
of delays. In each model patients were assigned an integer value based on days 
between index and their earliest missed opportunity. If no delay occured the 
duration was 0 days. For these results a linear model was used to estimate the 
days of duration

The following risk model pertains to all observations (CCAE, MDCR and Medicaid)

```{r, echo = FALSE}

ssd_miss_risk_models$miss_dur_res %>% 
  mutate(`Estimate (Days)` = paste0(formatC(est, digits = 3, format = "g", flag= "#"),
                                    " (",
                                    formatC(low, digits = 3, format = "g", flag= "#"),
                                    "-",
                                    formatC(high, digits = 3, format = "g", flag= "#"),")")) %>% 
  inner_join(better_labels) %>% 
  select(label, `Estimate (Days)`) %>% 
  kableExtra::kable() %>% 
  kableExtra::kable_styling(full_width = F)
```

The following risk model pertains to Medicaid patients

```{r, echo = FALSE}

ssd_miss_risk_models$miss_dur_res_med %>% 
  mutate(`Estimate (Days)` = paste0(formatC(est, digits = 3, format = "g", flag= "#"),
                                    " (",
                                    formatC(low, digits = 3, format = "g", flag= "#"),
                                    "-",
                                    formatC(high, digits = 3, format = "g", flag= "#"),")")) %>%   inner_join(better_labels) %>% 
  select(label, `Estimate (Days)`) %>% 
  kableExtra::kable() %>% 
  kableExtra::kable_styling(full_width = F)
```
