---
title: "Risk Factor Report"
date: '`r strftime(Sys.time(), format = "%B %d, %Y")`'
output: html_document
params:
  cond:
    value: x
---

```{r setup, include=FALSE}
knitr::opts_chunk$set(
      echo    = FALSE
    , warning = FALSE
    , message = FALSE
)

library(tidyverse)
library(kableExtra)
library(ggplot2)
library(lubridate)

# params <- list()
# params$cond <- "dengue"

# load delay_parms
load("/Shared/AML/params/final_delay_params_kaiser.RData")

delay_params <- final_delay_params[[proj_name]]
delay_params$cp <- as.numeric(stringr::str_split(proj_name, "_")[[1]][4]) + 1
delay_params$out_path <- paste0(final_delay_params[[proj_name]]$out_path, "delay_window_1_", delay_params$cp - 1, "/")

risk_model_base_path <- paste0(delay_params$out_path,"risk_models/")

# load results data
# load("/Volumes/AML/small_dbs/tb/truven/enroll_restrict_365/delay_results/risk_models/ssd_miss_risk_models.RData")
load(paste0(risk_model_base_path,"ssd_miss_risk_models.RData"))

# setup better labels
better_labels <- tribble(~term,~label,
                         '(Intercept)', '(Intercept)'  ,
                         'age_cat(17,34]', 'Age 18-34'  ,
                         'age_cat(34,44]', 'Age 35-44'  ,
                         'age_cat(44,54]', 'Age 45-54'  ,
                         'age_cat(54,64]', 'Age 55-64'  ,
                         'age_cat(64,130]', 'Age >= 65'  ,
                         'sexFemale', 'Female'  ,
                         "weekendTRUE", "Weekend Visit",
                         "fever_100", "Fever (>=100F) recorded during visit")

# better_labels <- better_labels %>% 
#   bind_rows(ssd_miss_risk_models$miss_opp_res %>% 
#               select(term) %>% 
#               filter(grepl("setting_label", term)) %>% 
#               mutate(label = stringr::str_remove_all(term, "setting_label")))
```


# Delay Risk Factor Report for `r params$cond`

### Missed Opportunities

The following tables depicts results for the risk model for experiencing a missed 
opportunity at a given visit. All missed visits and index dates are included in 
this model with an outcome of 1 assigned to missed opportunities and 0 to index 
diagnoses.

The following risk model pertains to all observations (CCAE, MDCR and Medicaid)

```{r, echo = FALSE}

ssd_miss_risk_models$miss_opp_res %>% 
  mutate(`Odds Ratio` = paste0(formatC(est, digits = 3, format = "g", flag= "#"),
                               " (",
                               formatC(low, digits = 3, format = "g", flag= "#"),
                               "-",
                               formatC(high, digits = 3, format = "g", flag= "#"),")")) %>% 
  inner_join(better_labels) %>% 
  select(label, `Odds Ratio`) %>% 
  kableExtra::kable() %>% 
  kableExtra::kable_styling(full_width = F)
```
Note: models also adjusted for year and month of visit.
