---
title: "Excess Antibiotics Before Cocci"
output: html_notebook
---

```{r, include = FALSE, echo = FALSE, message=FALSE, warning=FALSE}
library(kableExtra)
library(knitr)
library(tidyverse)
load("~/Data/projects/excess_abx/cocci/data/report_data.RData")

```

This document summarizes estimates for unecessary antibiotics recieved before a diagnosis of
coccidioidomycosis.

There were a total of `R nrow(index_dates)` patients with cocci who could be followed
for at least one year prior to their index diagnosis.

We considered a `R weekly_cp`-week window prior to diagnosis as the diagnostic opportunity 
window where unecessary antibiotics associated with diagnostic delays may have been
recieved.

The following plot depicts counts of the number of perscriptions each week before
diagnosis, for each of the relevant antibiotic types

```{r, echo = FALSE}
p1
```

The following plot depicts expected trends for the number of antibiotics received
based on data 14-52 weeks prior to diagnosis, using linear, quadratic and cubic trends.
```{r, echo = FALSE}
p2
```

The following plots depicts the number of antibiotics estimated to be in excess 
based on the expected trends depicted above.
```{r, echo = FALSE}
p3
```

## Bootstrapping results

To estimate the number of excess antibiotics while accounting for uncertainty in the
expected trend we utilized the following bootstrapping approach

1) Draw a bootstrapped sample of patients
2) Calculate the number of antibiotics each week
3) Estimate expected trends over the 14-52 weeks prior to diagnosis for each trend type
4) Compute the excess number of antibiotics as the difference between the observed
   number of antibiotics and the expected trend (extrapolated to the period between
   1-13 weeks prior to diagnosis)
   
The above procedure was repeated 1000 times.

### Linear Models

The following figure summarizes expected trends for the number of antibiotics
based on a linear model. The blue line depicts the mean trend across models and 
the gray band depicts a 95% confidence band.

```{r, echo = FALSE}
lm_res_plots$p2
```

### Quadratic Models

The following figure summarizes expected trends for the number of antibiotics
based on a quadratic model. The blue line depicts the mean trend across models and 
the gray band depicts a 95% confidence band.

```{r, echo = FALSE}
quad_res_plots$p2
```

### Cubic Models

The following figure summarizes expected trends for the number of antibiotics
based on a cubic model. The blue line depicts the mean trend across models and 
the gray band depicts a 95% confidence band.


```{r, echo = FALSE}
cubic_res_plots$p2
```

### Excess Antibiotics by Week

```{r, echo = FALSE}
p4
```


```{r, echo = FALSE}
p5
```
### Aggregate Number of Excess Antibiotics Before Diagnosis

The following table depicts the total number of excess antibiotics recieved by 
antibiotic and model type:

```{r, echo = FALSE}
excess_res1 %>% 
  knitr::kable() %>% 
  kableExtra::kable_styling()
```

The following table depicts the % of antibiotics precribed in the 13-weeks before
diagnosis that were estimated to be in excess by antibiotic and model type:

```{r, echo = FALSE}
excess_res2 %>% 
  knitr::kable() %>% 
  kableExtra::kable_styling()
```


## Patients Metrics for Reciept of Unecessary Antibiotics

In order to estimate the number of patients who recieved an unecessary antibiotic
we performed the following bootstrapping-based analysis:

1) Estimate the expected trend based on a bootstrapped sample of patients, and
   compute the estimated number of excess antibiotics (as described above).
2) Return to the aggregate sample of patients; each week draw the estimated number
   of excess antibiotics by antibiotic type.
3) Compute corresponding metrics and aggregate across trials.


```{r, echo = FALSE}
tibble(metric = c("Number of Patients with Excess Antibiotic",
                  "% of Patients with Excess Antibiotic",
                  "Excess Antibiotics per patient (all patients)",
                  "Excess Antibiotics per patient (patients w/ excess)"),
       
       lm = c(paste0(lm_stats$n_excess_patients$n_excess_patients," (",
                     lm_stats$n_excess_patients$n_excess_patients_lo,", ",
                     lm_stats$n_excess_patients$n_excess_patients_hi,")"),
              
              paste0(round(lm_stats$frac_excess_patients$n_excess_patients,2)," (",
                     round(lm_stats$frac_excess_patients$n_excess_patients_lo,2),", ",
                     round(lm_stats$frac_excess_patients$n_excess_patients_hi,2),")"),
              
              paste0(round(lm_stats$mean_excess_per_patient_all$mean_excess_per_patient,3)," (",
                     round(lm_stats$mean_excess_per_patient_all$mean_excess_per_patient_lo,3),", ",
                     round(lm_stats$mean_excess_per_patient_all$mean_excess_per_patient,3),")"),
              
              paste0(round(lm_stats$mean_excess_per_excess_patient$mean_excess_per_patient,3)," (",
                     round(lm_stats$mean_excess_per_excess_patient$mean_excess_per_patient_lo,3),", ",
                     round(lm_stats$mean_excess_per_excess_patient$mean_excess_per_patient,3),")")
       ),
       
       quad = c(paste0(quad_stats$n_excess_patients$n_excess_patients," (",
                       quad_stats$n_excess_patients$n_excess_patients_lo,", ",
                       quad_stats$n_excess_patients$n_excess_patients_hi,")"),
                
                paste0(round(quad_stats$frac_excess_patients$n_excess_patients,2)," (",
                       round(quad_stats$frac_excess_patients$n_excess_patients_lo,2),", ",
                       round(quad_stats$frac_excess_patients$n_excess_patients_hi,2),")"),
                
                paste0(round(quad_stats$mean_excess_per_patient_all$mean_excess_per_patient,3)," (",
                       round(quad_stats$mean_excess_per_patient_all$mean_excess_per_patient_lo,3),", ",
                       round(quad_stats$mean_excess_per_patient_all$mean_excess_per_patient,3),")"),
                
                paste0(round(quad_stats$mean_excess_per_excess_patient$mean_excess_per_patient,3)," (",
                       round(quad_stats$mean_excess_per_excess_patient$mean_excess_per_patient_lo,3),", ",
                       round(quad_stats$mean_excess_per_excess_patient$mean_excess_per_patient,3),")")
       ),
       
       cubic = c(paste0(cubic_stats$n_excess_patients$n_excess_patients," (",
                        cubic_stats$n_excess_patients$n_excess_patients_lo,", ",
                        cubic_stats$n_excess_patients$n_excess_patients_hi,")"),
                 
                 paste0(round(cubic_stats$frac_excess_patients$n_excess_patients,2)," (",
                        round(cubic_stats$frac_excess_patients$n_excess_patients_lo,2),", ",
                        round(cubic_stats$frac_excess_patients$n_excess_patients_hi,2),")"),
                 
                 paste0(round(cubic_stats$mean_excess_per_patient_all$mean_excess_per_patient,3)," (",
                        round(cubic_stats$mean_excess_per_patient_all$mean_excess_per_patient_lo,3),", ",
                        round(cubic_stats$mean_excess_per_patient_all$mean_excess_per_patient,3),")"),
                 
                 paste0(round(cubic_stats$mean_excess_per_excess_patient$mean_excess_per_patient,3)," (",
                        round(cubic_stats$mean_excess_per_excess_patient$mean_excess_per_patient_lo,3),", ",
                        round(cubic_stats$mean_excess_per_excess_patient$mean_excess_per_patient,3),")")
                 
       )) %>% 
    knitr::kable() %>% 
  kableExtra::kable_styling()
```


The following table depicts the fraction of patients who recieved an unecessary antibiotic 
by type:

```{r, echo = FALSE}
tmp_lm <- lm_stats$frac_excess_patients_by_type %>% 
  mutate_at(vars(n_excess_patients:n_excess_patients_hi),~round(.,2)) %>% 
  mutate(lm = paste0(n_excess_patients, " (",n_excess_patients_lo,", ",n_excess_patients_hi,")")) %>% 
  select(name, lm)


tmp_quad <- quad_stats$frac_excess_patients_by_type %>% 
  mutate_at(vars(n_excess_patients:n_excess_patients_hi),~round(.,2)) %>% 
  mutate(quad = paste0(n_excess_patients, " (",n_excess_patients_lo,", ",n_excess_patients_hi,")")) %>% 
  select(name, quad)

tmp_cubic <- cubic_stats$frac_excess_patients_by_type %>% 
  mutate_at(vars(n_excess_patients:n_excess_patients_hi),~round(.,2)) %>% 
  mutate(cubic = paste0(n_excess_patients, " (",n_excess_patients_lo,", ",n_excess_patients_hi,")")) %>% 
  select(name, cubic)

tmp_lm %>% 
  inner_join(tmp_quad, by = join_by(name)) %>% 
  inner_join(tmp_cubic, by = join_by(name)) %>% 
  knitr::kable() %>% 
  kableExtra::kable_styling()
```

The following table depicts the distribution in the number of unecessary
antibiotics individuals recieved:
```{r, echo = FALSE}
tmp_lm <- lm_stats$n_excess_abx_by_patient_count %>% 
  mutate_at(vars(n_mean:n_hi),~round(.,2)) %>% 
  mutate(lm = paste0(n_mean, " (",n_lo,", ",n_hi,")")) %>% 
  select(n_excess, lm)

tmp_quad <- quad_stats$n_excess_abx_by_patient_count %>% 
  mutate_at(vars(n_mean:n_hi),~round(.,2)) %>% 
  mutate(quad = paste0(n_mean, " (",n_lo,", ",n_hi,")")) %>% 
  select(n_excess, quad)

tmp_cubic <- cubic_stats$n_excess_abx_by_patient_count %>% 
  mutate_at(vars(n_mean:n_hi),~round(.,2)) %>% 
  mutate(cubic = paste0(n_mean, " (",n_lo,", ",n_hi,")")) %>% 
  select(n_excess, cubic)

tmp_lm %>% 
  inner_join(tmp_quad, by = join_by(n_excess)) %>% 
  inner_join(tmp_cubic, by = join_by(n_excess)) %>% 
  knitr::kable() %>% 
  kableExtra::kable_styling()
```

